---
title: "Syngene QC report"
subtitle: "cells in S061"
author: "Florian Heigwer"
date: "4 November 2016"
output:
  pdf_document: default
  html_document: default
---

```{r setup,echo=FALSE,error=FALSE,warning=FALSE,include=FALSE}
#define_analysis_parameters
set="S061"
feat="cells"
```


```{r echo=FALSE,error=FALSE,warning=FALSE,include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RPostgreSQL)
library(FitAR)
test_db <- src_postgres(dbname = "incell2000_test",
                        host = "b110-sc2sn01",
                        user = "florianH",
                        password = "x!Kl9R_p7XZYjLhg")

#helper function for Z-Prime-factor
z.prime <- function(pos,neg){
  z=1-(
      (3*sd(pos,na.rm=T)+3*sd(neg,na.rm=T))/abs(mean(pos,na.rm=T)-mean(neg,na.rm=T))
    )
  return(tbl_df(z) %>% rename(zprimefactor=value))
}
#helper function for Z-factor
z.fact <- function(pos,neg){
  z=1-(
      (3*sd(pos,na.rm=T)+3*sd(neg,na.rm=T))/abs(mean(pos,na.rm=T)-mean(neg,na.rm=T))
    )
  return(tbl_df(z) %>% rename(zfactor=value))
}
#normalization function that normalizes each plate to its median except the control plates who get normalized by the average of all sample plates
norm_to_median<-function(x){
  screenval <- x %>% ungroup() %>% select(screen) %>% distinct() %>% unlist(use.names = F)
  featureval <- x %>% ungroup() %>% select(feature) %>% distinct() %>% unlist(use.names = F)
  val <- ref_vals %>% filter(screen==screenval,feature==featureval) %>% select(m) %>% unlist(use.names = F)
  if(filter(x,kind=="sample") %>% n_distinct() > 1){
    return(x %>% mutate(value=value/median(value[content=="sample"],na.rm=T)))
  }else{
    return(x %>% mutate(value=value/val))
  }
}
#z-transform each data point by the median of the negative controls of the control plates and the mad of the rluc controls of each sample plate
norm_to_ctrlplates<-function(x){
  m <- 
    x %>% 
      filter(kind=="ctrl",content=="rluc") %>% 
      summarise(m=median(value,na.rm=T))
  s <- 
    x %>% 
    filter(kind=="sample",content=="rluc") %>% 
    summarise(s=mad(value,na.rm=T))
  
  x %>% mutate(value=(value-m$m)/s$s)
}
#helper function to find design correlations
f<-function(x){
  tbl_df(cor(x$`1`,x$`2`,use = "p",method = "spearman"))
}
#helper function to count all plates in the screening set, which could no be well replicated
collect_stats<-function(x){
  if(nrow(x %>% filter(correlates=="bad"))<1){
    x %>% mutate(count=NA)
  }else{
    x %>% filter(correlates=="bad") %>% mutate(count=n())
  }
}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

#read in annotation
#synanno <- read_delim("final_machine_readable_annoation.txt",delim = "\t",col_types = cols(.default = col_character()))
aggregated_data_db <- tbl(test_db,"D1086_trimmed_mean")
syngene_annotation_db <- tbl(test_db,"D1086_annotation") %>% collect()

sumfunc<-function(x){
  if(is.numeric(x)){
    return(mean(x))
  }else{
    return(x[1])
  }
}

syndata <- 
  aggregated_data_db %>% 
  select(   -barcode,-ends_with(".sd")) %>%
  filter(  screen==set    ) %>%
  collect(n=Inf) %>%
  mutate(well=gsub(well,pattern="_",replacement = "" ,perl = T)) %>% 
  mutate(plate=gsub(plate,pattern="Crtl",replacement = "CTRL" ,perl = T)) %>% 
  group_by(screen,plate,well,field) %>%
  summarise_all(mean) %>% 
  ungroup() %>%
  left_join(syngene_annotation_db) %>%
  gather(feature,value,-well,-plate,-screen,-field,-content,-id,-fbgn,-gene_symbol,-hd3plate,-hd3well,-hd3content,-hd3query_id,-hd3fbgn,-hd3gene) %>%
  ungroup()

```

## Data formatting and Normalization

In a first step, all data is filtered to only those data of interest to this analysis. We can therfore filter for the interesting feature we want to quality control and the screen whoe quality we want to assess. Further the data are normilzed the follwoing way:

1.  We collect the trimmed mean with 5% quantiles trimmed of every well

2.  We transform the data by a glog from the FitAR package with an alpha of the 3% quantile of the data

2.  We devide each plate and each feature by the median value observed in this plate

3.  We transform each features value into the robust Z-Score with respect to the non-targeting controls

4.  We have a quick look at the data.

```{r normalize,echo=FALSE,warning=FALSE,error=FALSE}

ref_vals <- 
  syndata %>%  
  mutate(kind=if_else(grepl("CTRL",plate),"ctrl","sample"),
         value=glog(value,a = quantile(value,0.03,na.rm=T))) %>%
  filter(kind=="sample") %>%
  group_by(screen,feature) %>%
  summarise(m=median(value[content=="sample"],na.rm=T)) %>%
  ungroup() 

syndata %<>%
  mutate(kind=if_else(grepl("CTRL",plate),"ctrl","sample"),
         rawvalue=value,
         value=glog(value,a = quantile(value,0.03,na.rm=T))
         ) %>%
  group_by(screen,plate,feature) %>%
  do(norm_to_median(.)) %>%
  group_by(feature,screen) %>%
  do(norm_to_ctrlplates(.)) %>%
  mutate(design=ifelse(grepl("^20",plate),2,1)) %>% 
  extract(plate,"tmp","(\\d{2}$)",remove = F) %>% 
  mutate(targetid=paste(tmp,well,sep = "_")) %>% 
  group_by(screen,plate,well,feature) %>% 
  mutate(value=mean(value,na.rm=T),rawvalue=mean(rawvalue,na.rm=T)) %>%
  select(-field) %>% 
  ungroup() %>% 
  distinct()


```

\pagebreak

## Control dispersion

As the first quality control, lets plot How the controls were dispersed in the different screens. Three Quality cirteria can be deduced here.

1. Did normalization bring the negative controls (Rluc) onto one straight line?

2. Act all controls as expected in each plate of the screen?

3. Are all controls well dispersed?

```{r, error=FALSE, warning=FALSE,echo=FALSE}
#First a scatterplot

# of raw data
p1 <- syndata %>% 
  filter(content != "sample",feature=="cells") %>% 
  ggplot(aes(x=plate,y=rawvalue,col=content)) + 
    geom_point() + 
    geom_hline(yintercept = median(syndata$rawvalue[syndata$content=="rluc"])) +
    #facet_wrap("screen","feature") + 
    ggtitle("Control dispersion in raw data") + 
    theme(
      axis.text.x=element_text(angle=90, size=6),
      panel.background = element_rect(fill = "white")
    ) 

#of normalized data
p2 <- syndata %>% 
  filter(content != "sample",feature=="cells") %>% 
  ggplot(aes(x=plate,y=value,col=content)) + 
    geom_point() + 
    geom_hline(yintercept = median(syndata$value[syndata$content=="rluc"])) + 
    #facet_wrap("screen","feature") + 
    ggtitle("Control dispersion in normalized data") + 
    theme(
      axis.text.x=element_text(angle=90, size=6),
      panel.background = element_rect(fill = "white")
    ) 

#second a densityplot
#of raw data
p3 <- syndata %>% 
  filter(content != "sample",feature=="cells") %>% 
  ggplot(aes(rawvalue,fill=content, alpha=0.5)) + 
    geom_density() + 
    #facet_wrap("screen","feature",scales="free") + 
    ggtitle("Control dispersion in raw data") + 
    theme_classic()
#of normalized data
p4 <- syndata %>% 
  filter(content != "sample",feature=="cells") %>% 
  ggplot(aes(value,fill=content, alpha=0.5)) + 
    geom_density() + 
   # facet_wrap("screen","feature",scales="free") + 
    ggtitle("Control dispersion in normalized data") + 
    theme_classic()

multiplot(p1, p2,  cols=1)

multiplot(p3, p4, cols=1)
```

\pagebreak

## Z' factor analysis for each plate

Using the Z-factor analysis we can assess if our assay has worked for the feature we chose. There we ask how well our controls are separated from each other. A factor between 0.5 and 1 here denotes an excellent separation of controls and that the assay works great. Values between 0.5 and 0 denote an okish assay. Everything else marks the plate as failing in this analysis. However we are very stringend here and call any plate with an Z-factor (between neutral and postivie controls) or Z-prime factor (between negative and positive controls) lower than 0.5 failed.

```{r ,error=F,warning=F,echo=FALSE}

# let's plot the Z' factor between gap1 and thread (one should promote growth, the other should decrease it)
p1 <- syndata %>% 
  filter(feature=="cells") %>%
  group_by(screen,feature,plate) %>%
  do(z.prime(pos=.$value[.$content=="gap1"],neg=.$value[.$content=="thread"])) %>%
  mutate(passedQC=if_else(zprimefactor>=0.5,"passed","failed")) %>%
  ggplot(aes(x=plate,y=zprimefactor, fill=passedQC)) + geom_bar(stat="identity") + 
  geom_hline(yintercept = 0.5, col="red") + 
  scale_y_continuous(limits = c(-1,1)) + 
    ggtitle("Control Z'-factor between gap1 and diap1") +
    theme(
      axis.text.x=element_text(angle=90, size=6),
      panel.background = element_rect(fill = "white")
    ) 

# to be more stringend we can also plot the Z factor between rluc and thread (one should do nothing, the other should kill all cells)
p2 <- syndata %>% 
  filter(feature=="cells") %>%
  group_by(screen,feature,plate) %>%
  do(z.fact(pos=.$value[.$content=="rluc"],neg=.$value[.$content=="thread"])) %>%
  mutate(passedQC=if_else(zfactor>=0.5,"passed","failed")) %>%
  ggplot(aes(x=plate,y=zfactor, fill=passedQC)) + geom_bar(stat="identity") + 
  geom_hline(yintercept = 0.5, col="red") + 
  scale_y_continuous(limits = c(-1,1)) +
    ggtitle("Control Z-factor between RLUC and diap1")  +
    theme(
      axis.text.x=element_text(angle=90, size=6),
      panel.background = element_rect(fill = "white")
    ) 

multiplot(p1, p2,  cols=1)
```

\pagebreak

## Design correlation

Now that we know how normalization worked and how the variance spreads along the plates we can have a glimpse on the design reproducability between the first and second designs targeting all genes in the library.

```{r, error=FALSE, warning=FALSE,echo=FALSE}

woqueryeffect <- syndata %>% group_by(feature) %>% mutate(value=(value-median(value,na.rm=T))/mad(value,na.rm=T)) %>% ungroup()

designcorr <- 
  woqueryeffect %>% 
  ungroup() %>% 
  filter(content=="sample",kind=="sample") %>% 
  mutate(design=ifelse(grepl("HD31",id),1,2)) %>% 
  extract(id,"hdid",regex = "(\\d{5})$") %>%
  select(hdid,design, feature, value) %>%
  spread(design,value) %>% 
  complete(hdid,feature) %>% 
  group_by(hdid) %>%
  do(f(.)) %>% 
  ungroup()

samplids=designcorr %>% sample_n(6840) %>% select(hdid) %>% unlist(use.names = F)
rand=rbind.data.frame(cbind(samplids,rep(1,times=length(samplids))),cbind(samplids,rep(2,times=length(samplids))))
rand=rand[sample(nrow(rand)),]
names(rand)=c("nums","designs")

randcorr <- 
  woqueryeffect %>% 
  ungroup() %>% 
  filter(content=="sample",kind=="sample") %>% 
  mutate(design=ifelse(grepl("HD31",id),1,2)) %>% 
  extract(id,"hdid",regex = "(\\d{5})$") %>%
  select(hdid,design, feature, value) %>%
  group_by(feature) %>% 
  mutate(hdid=as.character(rand$nums),design=rand$designs) %>% 
  spread(design,value) %>%  
  group_by(hdid) %>% 
  do(f(.)) %>%
  ungroup() %>% 
  select(hdid,randvalue=value)

designcorr %<>% ungroup() %>% left_join(randcorr ) %>% gather(type,val,-hdid) 

d1 <- designcorr %>% filter(type=="value",is.finite(val)) %>% select(val) %>% unlist(use.names = F) %>% density()
d2 <- designcorr %>% filter(type=="randvalue",is.finite(val)) %>% select(val) %>% unlist(use.names = F) %>% density()

d1_med <- designcorr %>% filter(type=="value",is.finite(val)) %>% select(val) %>% unlist(use.names = F) %>% median()
d2_med <- designcorr %>% filter(type=="randvalue",is.finite(val)) %>% select(val) %>% unlist(use.names = F) %>% median()

designcorr %>% ggplot(aes(val, fill=type,alpha=0.5)) + geom_density() +geom_vline(xintercept = c(d1_med,d2_med))
```


We find a random correlation median of:

```{r , error=FALSE, warning=FALSE,echo=FALSE}
cat(d2_med)
```

And a sample correlations median of:

```{r , error=FALSE, warning=FALSE,echo=FALSE}
cat(d1_med)
if(d1_med-d2_med<0.3){
  cat("Warning: design correlations are close to random correlations.")
}else{
  cat("Message: design correlations are good.")
}
poi=0.3
```


```{r, error=FALSE, warning=FALSE,echo=FALSE,include=FALSE}
forscatter <- 
  woqueryeffect %>% 
  ungroup() %>% 
  filter(content=="sample",kind=="sample") %>% 
  mutate(design=ifelse(grepl("HD31",id),1,2)) %>% 
  extract(id,"hdid",regex = "(\\d{5})$") %>% 
  select(hdid,targetid,design, feature, value) %>% 
  arrange(hdid) %>% 
  spread(feature,value) %>% 
  select(targetid,hdid,design,cells) %>% 
  spread(design,cells) %>% 
  left_join(designcorr %>% filter(type=="value")) %>%
  mutate(correlates=ifelse(val<poi,"bad","good"))
```

Plot the scatter of replicates using cell count data:

```{r, error=FALSE, warning=FALSE,echo=FALSE}
forscatter %>%
  ggplot(aes(x=`1`,y=`2`,col=correlates)) + 
  geom_point() +
  geom_smooth(method = 'lm') +
  geom_abline(slope = 1,intercept = c(0,0),col="red")
```

Plot which wells were not correlating

```{r, error=FALSE, warning=FALSE,echo=FALSE}
forscatter %>% 
  separate(targetid,c("plate","well")) %>%
  extract(well,c("row","col"),regex = "([A-Z])(\\d+)") %>%
  mutate(col=as.numeric(col)) %>%
  complete(plate,row,col) %>%
  arrange(plate,row,col) %>%
  mutate(row=factor(row,levels = rev(unique(row))),col=factor(col,ordered = T)) %>%
  ggplot(aes(col, 
             row, 
             col=correlates,
             fill=correlates
  )
  ) + 
  geom_tile() + 
  facet_wrap(~plate)
```

Plot an overview which cells in general do not correlate:

```{r, error=FALSE, warning=FALSE,echo=FALSE}
f<-function(x){
  if(nrow(x %>% filter(correlates=="bad"))<1){
    x %>% mutate(count=NA)
  }else{
    x %>% filter(correlates=="bad") %>% mutate(count=n())
  }
}

forscatter %>% 
  separate(targetid,c("plate","well")) %>%
  extract(well,c("row","col"),regex = "([A-Z])(\\d+)") %>%
  mutate(col=as.numeric(col)) %>%
  complete(plate,row,col) %>%
  group_by(col,row) %>%
  do(f(.)) %>%
  select(col,row,count) %>%
  ungroup() %>%
  distinct() %>%
  arrange(row,col) %>%
  mutate(row=factor(row,levels = rev(unique(row))),col=factor(col,ordered = T)) %>%
  ggplot(aes(col,row,fill=count)) + 
  geom_tile()

```

