---
title: "Syngene short QC report S060"
output: pdf_document
---

```{r ,echo=FALSE,error=FALSE,warning=FALSE,include=FALSE}

#define_analysis_parameters
set="S060"
feat="cells"

```

```{r setup,echo=FALSE,error=FALSE,warning=FALSE,include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RPostgreSQL)
library(FitAR)
test_db <- src_postgres(dbname = "incell2000_test",
                        host = "b110-sc2sn01",
                        user = "florianH",
                        password = "x!Kl9R_p7XZYjLhg")

#helper function for Z-Prime-factor
z.prime <- function(pos,neg){
  z=1-(
      (3*sd(pos,na.rm=T)+3*sd(neg,na.rm=T))/abs(mean(pos,na.rm=T)-mean(neg,na.rm=T))
    )
  return(tbl_df(z) %>% rename(zprimefactor=value))
}
#helper function for Z-factor
z.fact <- function(pos,neg){
  z=1-(
      (3*sd(pos,na.rm=T)+3*sd(neg,na.rm=T))/abs(mean(pos,na.rm=T)-mean(neg,na.rm=T))
    )
  return(tbl_df(z) %>% rename(zfactor=value))
}
#normalization function that normalizes each plate to its median except the control plates who get normalized by the average of all sample plates
norm_to_median<-function(x){
  screenval <- x %>% ungroup() %>% select(screen) %>% distinct() %>% unlist(use.names = F)
  featureval <- x %>% ungroup() %>% select(feature) %>% distinct() %>% unlist(use.names = F)
  val <- ref_vals %>% filter(screen==screenval,feature==featureval) %>% select(m) %>% unlist(use.names = F)
  if(filter(x,kind=="sample") %>% n_distinct() > 1){
    return(x %>% mutate(value=value/median(value[content=="sample"],na.rm=T)))
  }else{
    return(x %>% mutate(value=value/val))
  }
}
#z-transform each data point by the median of the negative controls of the control plates and the mad of the rluc controls of each sample plate
norm_to_ctrlplates<-function(x){
  m <- 
    x %>% 
      filter(kind=="ctrl",content=="rluc") %>% 
      summarise(m=median(value,na.rm=T))
  s <- 
    x %>% 
    filter(kind=="sample",content=="rluc") %>% 
    summarise(s=mad(value,na.rm=T))
  
  x %>% mutate(value=(value-m$m)/s$s)
}
#helper function to find design correlations
f<-function(x){
  tbl_df(cor(x$`1`,x$`2`,use = "p",method = "spearman"))
}
#helper function to count all plates in the screening set, which could no be well replicated
collect_stats<-function(x){
  if(nrow(x %>% filter(correlates=="bad"))<1){
    x %>% mutate(count=NA)
  }else{
    x %>% filter(correlates=="bad") %>% mutate(count=n())
  }
}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}



#read in annotation
#synanno <- read_delim("final_machine_readable_annoation.txt",delim = "\t",col_types = cols(.default = col_character()))
aggregated_data_db <- tbl(test_db,"D1086_trimmed_mean")
syngene_annotation_db <- tbl(test_db,"D1086_annotation") %>% collect()

syndata <- 
  aggregated_data_db %>% 
  select(   -barcode      ,-ends_with(".sd")) %>%
  filter(  screen==set    ) %>%
  collect(n=Inf) %>%
  mutate(well=gsub(well,pattern="_",replacement = "" ,perl = T)) %>% 
  mutate(plate=gsub(plate,pattern="Crtl",replacement = "CTRL" ,perl = T)) %>% 
  group_by(screen,plate,well,field) %>%
  summarise_all(mean) %>% 
  ungroup() %>%
  left_join(syngene_annotation_db) %>%
  gather(feature,value,-well,-plate,-screen,-field,-content,-id,-fbgn,-gene_symbol,-hd3plate,-hd3well,-hd3content,-hd3query_id,-hd3fbgn,-hd3gene) %>%
  ungroup()
  
ref_vals <- 
  syndata %>%  
  mutate(kind=if_else(grepl("CTRL",plate),"ctrl","sample"),
         value=glog(value,a = quantile(value,0.03,na.rm=T))) %>%
  filter(kind=="sample") %>%
  group_by(screen,feature) %>%
  summarise(m=median(value[content=="sample"],na.rm=T)) %>%
  ungroup() 

syndata %<>%
  mutate(kind=if_else(grepl("CTRL",plate),"ctrl","sample"),
         rawvalue=value,
         value=glog(value,a = quantile(value,0.03,na.rm=T))
         ) %>%
  group_by(screen,plate,feature) %>%
  do(norm_to_median(.)) %>%
  group_by(feature,screen) %>%
  do(norm_to_ctrlplates(.)) %>%
  mutate(design=ifelse(grepl("^20",plate),2,1)) %>% 
  extract(plate,"tmp","(\\d{2}$)",remove = F) %>% 
  mutate(targetid=paste(tmp,well,sep = "_")) %>% 
  group_by(screen,plate,well,feature) %>% 
  mutate(value=mean(value,na.rm=T),rawvalue=mean(rawvalue,na.rm=T)) %>%
  select(-field) %>% 
  ungroup() %>% 
  distinct()
```

## Z' factor analysis for each plate

Using the Z-factor analysis we can assess if our assay has worked for the feature we chose. There we ask how well our controls are separated from each other. A factor between 0.5 and 1 here denotes an excellent separation of controls and that the assay works great. Values between 0.5 and 0 denote an okish assay. Everything else marks the plate as failing in this analysis. However we are very stringend here and call any plate with an Z-factor (between neutral and postivie controls) or Z-prime factor (between negative and positive controls) lower than 0.5 failed.

```{r ,error=F,warning=F,echo=FALSE}

# let's plot the Z' factor between gap1 and thread (one should promote growth, the other should decrease it)
passedZprime <- syndata %>% 
  filter(feature=="cells") %>%
  group_by(screen,feature,plate) %>%
  do(z.prime(pos=.$value[.$content=="gap1"],neg=.$value[.$content=="thread"])) %>%
  mutate(passedQC=if_else(zprimefactor>=0.5,"passed","failed")) %>%
  filter(passedQC=="passed") %>%
  ungroup() %>%
  summarise(count=n())

# to be more stringend we can also plot the Z factor between rluc and thread (one should do nothing, the other should kill all cells)
passedZfac <- syndata %>% 
  filter(feature=="cells") %>%
  group_by(screen,feature,plate) %>%
  do(z.fact(pos=.$value[.$content=="rluc"],neg=.$value[.$content=="thread"])) %>%
  mutate(passedQC=if_else(zfactor>=0.5,"passed","failed")) %>%
  filter(passedQC=="passed") %>%
  ungroup() %>%
  summarise(count=n())

```

## Assay controls

Analysis reveals that:

```{r ,error=F,warning=F,echo=FALSE}
cat(passedZprime$count)
```

of 38 paltes passed the Z' factor treshold of 0.5.

and that

```{r ,error=F,warning=F,echo=FALSE}
cat(passedZfac$count)
```

of 38 paltes passed the Z factor treshold of 0.5.

## Design correlation

Now that we know how normalization worked and how the variance spreads along the plates we can have a glimpse on the design reproducability between the first and second designs targeting all genes in the library.

```{r, error=FALSE, warning=FALSE,echo=FALSE,include=FALSE}

woqueryeffect <- syndata %>% group_by(feature) %>% mutate(value=(value-median(value,na.rm=T))/mad(value,na.rm=T)) %>% ungroup()

designcorr <- 
  woqueryeffect %>% 
  ungroup() %>% 
  filter(content=="sample",kind=="sample") %>% 
  mutate(design=ifelse(grepl("HD31",id),1,2)) %>% 
  extract(id,"hdid",regex = "(\\d{5})$") %>%
  select(hdid,design, feature, value) %>%
  spread(design,value) %>% 
  complete(hdid,feature) %>% 
  group_by(hdid) %>%
  do(f(.)) %>% 
  ungroup()

samplids=designcorr %>% sample_n(6840) %>% select(hdid) %>% unlist(use.names = F)
rand=rbind.data.frame(cbind(samplids,rep(1,times=length(samplids))),cbind(samplids,rep(2,times=length(samplids))))
rand=rand[sample(nrow(rand)),]
names(rand)=c("nums","designs")

randcorr <- 
  woqueryeffect %>% 
  ungroup() %>% 
  filter(content=="sample",kind=="sample") %>% 
  mutate(design=ifelse(grepl("HD31",id),1,2)) %>% 
  extract(id,"hdid",regex = "(\\d{5})$") %>%
  select(hdid,design, feature, value) %>%
  group_by(feature) %>% 
  mutate(hdid=as.character(rand$nums),design=rand$designs) %>% 
  spread(design,value) %>%  
  group_by(hdid) %>% 
  do(f(.)) %>%
  ungroup() %>% 
  select(hdid,randvalue=value)

designcorr %<>% ungroup() %>% left_join(randcorr ) %>% gather(type,val,-hdid) 

d1 <- designcorr %>% filter(type=="value",is.finite(val)) %>% select(val) %>% unlist(use.names = F) %>% median()
d2 <- designcorr %>% filter(type=="randvalue",is.finite(val)) %>% select(val) %>% unlist(use.names = F) %>% median()

# look for points of intersection

```

We find a random correlation median of:

```{r , error=FALSE, warning=FALSE,echo=FALSE}
cat(d2)
```

And a sample correlations median of:

```{r , error=FALSE, warning=FALSE,echo=FALSE}
cat(d1)
if(d1-d2<0.3){
  cat("Warning: design correlations are close to random correlations.")
}else{
  cat("Messager: design correlations are good.")
}
poi=0.3
```

```{r , error=FALSE, warning=FALSE,echo=FALSE,include=FALSE}
forscatter <- 
  syndata %>% 
  ungroup() %>% 
  filter(content=="sample",kind=="sample") %>% 
  mutate(design=ifelse(grepl("HD31",id),1,2)) %>% 
  extract(id,"hdid",regex = "(\\d{5})$") %>% 
  select(hdid,targetid,design, feature, rawvalue) %>% 
  spread(feature,rawvalue) %>% 
  select_("targetid","hdid","design",feat) %>% 
  spread_("design",feat) %>% 
  left_join(designcorr %>% filter(type=="value")) %>%
  select(-type) %>%
  mutate(correlates=ifelse(val<poi,"bad","good")) %>% 
  separate(targetid,c("plate","well")) %>%
  extract(well,c("row","col"),regex = "([A-Z])(\\d+)") %>%
  mutate(col=as.numeric(col)) %>%
  complete(plate,row,col) %>%
  arrange(plate,row,col) %>%
  mutate(row=factor(row,levels = rev(unique(row))),col=factor(col,ordered = T))

badlycorrelating<-forscatter %>% filter(correlates=="bad") %>% ungroup() %>% summarise(n=n()) %>% unlist(use.names = F)

```

There we find that 

```{r ,error=F,warning=F,echo=FALSE}
cat(badlycorrelating)
```

wells do correlate worse than r = 0.3 .

These wells map the following way across the paltes of the screen:

```{r ,error=F,warning=F,echo=FALSE}

forscatter  %>%
  ggplot(aes(col, 
             row,
             fill=correlates
  )
  ) + 
  geom_tile() + 
  facet_wrap("plate") +
  theme(
        axis.text.x = element_text(angle = 90, hjust = 1, size=5,color="black"),
        axis.text.y = element_text(hjust = 1, size=5,color="black"),
        plot.title = element_text(lineheight=1, color="black", size=2)
        ) + 
  xlab('') +
  ylab('')

```

In general the cell seeding and anlysis can be controled on the mean of the two internal replicates:

```{r ,error=F,warning=F,echo=FALSE}

forscatter %>% 
  mutate(val=(`1`+`2`)/2) %>%
  ggplot(aes(col, 
             row,
             fill=val
  )
  ) + 
  geom_tile() + 
  #scale_fill_gradientn(colours = cm.colors(10, alpha = 1)) +
  facet_wrap("plate") +
  theme(
        axis.text.x = element_text(angle = 90, hjust = 1, size=5,color="black"),
        axis.text.y = element_text(hjust = 1, size=5,color="black"),
        plot.title = element_text(lineheight=1, color="black", size=2)
        ) + 
  xlab('') +
  ylab('')

```
