---
title: "sc_bulk_comparison"
author: "Florian Heigwer"
date: "7/27/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(ggpubr)
library(ggrastr)
library(patchwork)
library(ggrepel)
library(MASS)

theme_b110<-function(){
  theme_classic() +
  theme(
    axis.text=element_text(size = 10), 
    axis.title=element_text(size = 10),
    plot.title = element_text(size = 12,hjust = 0.5,face="bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size =10),
    legend.position = "bottom"
    )
}

sgi_blue    = '#5087C8'
sgi_yellow1 = '#F2EE35'
sgi_yellow2 = '#FED98E'
b110_grey   = '#808080'
b110_grey_light   = '#909090'
google_red='#dd4b39'
google_green='#0F9D58'
google_yellow='#F4B400'
google_blue='#4285F4'

```

## Figure 4B Summary statistics on population based interactions

```{r}

population_interaction_counts <- results_data %>% 
  as_tibble() %>% 
  unite("QueTarg",query_name,target_name,plate,well) %>%
  filter(fdr<0.1) %>%
  arrange(fdr,mpi) %>%
  group_by(QueTarg) %>%
  dplyr::count()

population_interaction_counts %>% 
   ungroup %>% dplyr::select(n) %>% table()

tabulated_data <- results_data %>% 
  as_tibble() %>% 
  unite("QueTarg",query_name,target_name,plate,well) %>%
  unite("Population",context,group) %>%
  filter(fdr<0.1,mpi<0) %>%
  dplyr::select(QueTarg,Population) %>%
  mutate(interacts=1) %>%
  spread(Population,interacts,fill=0)

a <- UpSetR::upset(
  as.data.frame(tabulated_data),
  sets = names(tabulated_data)[2:10],
  nintersects = 30,
  order.by = c("freq"), 
  decreasing = c(TRUE),
  sets.bar.color = sgi_blue
  )


tabulated_data <- results_data %>% 
  as_tibble() %>% 
  unite("QueTarg",query_name,target_name,plate,well) %>%
  unite("Population",context,group) %>%
  filter(fdr<0.1,mpi>0) %>%
  dplyr::select(QueTarg,Population) %>%
  mutate(interacts=1) %>%
  spread(Population,interacts,fill=0)

b <- UpSetR::upset(
  as.data.frame(tabulated_data),
  sets = names(tabulated_data)[2:10],
  nintersects = 30,
  order.by = c("freq"), 
  decreasing = c(TRUE),
  sets.bar.color = sgi_yellow2
  )

tabulated_data <- results_data %>% 
  as_tibble() %>% 
  unite("QueTarg",query_name,target_name,plate,well) %>%
  unite("Population",context,group) %>%
  filter(fdr<0.1) %>%
  dplyr::select(QueTarg,Population) %>%
  mutate(interacts=1) %>%
  spread(Population,interacts,fill=0)

c <- UpSetR::upset(
  as.data.frame(tabulated_data),
  sets = names(tabulated_data)[2:10],
  nintersects = 30,
  order.by = c("freq"), 
  decreasing = c(TRUE),
  sets.bar.color = b110_grey
  )

pdf("population_interactions_upset.pdf")
  print(a)
  print(b)
  print(c)
dev.off()

```

## Interesting interactions

Sudden gain of isolated cells of a specific phenotypic sub-class. Classes were changed manually and enrichments calculated by employing FlyEnrichR (https://maayanlab.cloud/FlyEnrichr/, see extra script gene_set_enrichment.R). The code below serves the purpose of manual exploration.

```{r}
sudden_gain_big <- 
  results_data %>% 
  as_tibble() %>% 
  unite("QueTarg",query_name,target_name,plate,well) %>%
  unite("Population",context,group) %>%
  filter(fdr<=0.1,mpi>0) %>%
  dplyr::select(QueTarg,Population) %>%
  mutate(interacts=1) %>%
  spread(Population,interacts,fill=0) %>%
  mutate(total =  rowSums(across(where(is.numeric)))) %>%
  filter(total==1, Isolated_Irregular_nucleus == 1) %>% # isolated condensed, isolated elongated isolated big, isolated irregular nucleus
  tidyr::separate(col=QueTarg,into=c("query_name","target_name","plate","well"),sep="_") %>%
  select_if(is.character)

# search surprisingly enriched query genes

sudden_gain_big %>% 
  dplyr::select(query_name) %>%
  table() %>% sort()

# search surprisingly enriched target genes
sudden_gain_big %>% 
  dplyr::select(target_name) %>%
  filter(!grepl("^Rp",target_name)) %>% 
  table() %>% sort(decreasing = T) %>%
  head(60) %>% names() %>% cat(sep="\n")


# check some interactions back in the bulk analysis and see which of the interesting single cell interactions were recovered in bulk analyses

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="swm",fdr<0.1,targetid=="09_L18")

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="swm",fdr<0.1,targetid=="09_O6")

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="S6k",targetid=="13_P22")%>% 
  arrange(fdr)

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="Sesn",targetid=="17_C20") %>% 
  arrange(fdr)

results_data %>%
  filter(query_name=="raptor",target_name=="mip120")%>% 
  arrange(fdr)

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="B52",fdr<0.2,targetid=="18_D18") 

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="brm",fdr<0.2,targetid=="13_J17") 

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="piwi",targetid=="11_G22") %>% arrange(fdr)

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="Cdc23",targetid=="16_P16") %>% arrange(fdr)

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="Rab1",targetid=="06_F22") %>% arrange(fdr)

interactions_stats_all_feats_df_18112019 %>%
  filter(query_name=="Rab1",targetid=="04_P7") %>% arrange(fdr)

```

## Call state specific interaction profile correlations

```{r}
state_spec_interaction_corrs <- results_data %>% 
  dplyr::select(plate,well,target_name,query_name,mpi,context,group) %>%
  unite("StateQue",context,group,query_name) %>%
  unite("PTarg",target_name,plate,well) %>%
  spread(PTarg,mpi) %>%
  column_to_rownames("StateQue") %>%
  corrr::correlate()

saveRDS(state_spec_interaction_corrs,"state_spec_interaction_corrs.rds")

state_spec_interaction_corrs_dropped <- state_spec_interaction_corrs %>% 
  corrr::shave() %>% 
  stretch() %>% 
  drop_na()

state_spec_interaction_corrs_dropped %>%
  filter(r>0.5,grepl("CG3847",x)|grepl("CG3847",y)) %>%
  arrange(-r)

state_spec_interaction_corrs_dropped %>%
  filter(r>0.7) %>%
  separate(x,c("namex","platex","wellx"),sep="_") %>%
    separate(y,c("namey","platey","welly"),sep="_") %>%
  select(namex,namey,r) %>%
  write_delim("simple_cor_stat_spec_0.7.tab",delim="\t")

saveRDS(state_spec_interaction_corrs_dropped,"state_spec_interaction_corrs_dropped.rds")
```

## Figure 4G State specific interactions of Rho1 and cell cycle regulators
# data wrangling

```{r interaction_filtering}

sc_Tlk_interactions_sig <- 
  results_data %>% 
  filter(query_name == "Rho1",fdr<0.1,target_name %in% c("geminin","aurB","osa","polo") ) %>%
  as_tibble()

targets<-sc_Tlk_interactions_sig %>% pull(target_name) %>% unique()


sc_Tlk_interactions_unfiltered <- 
  results_data %>% 
  filter(query_name == "Rho1",target_name %in% targets) %>% 
  as_tibble()


target_gene_list<- updated_target_genes %>% 
  as_tibble() %>%
  dplyr::select(plate,well,gene_symbol,hd3gene) %>%
  mutate(well=gsub("^(\\w)0(\\d)$","\\1\\2",well)) %>%
  unite("targetid",plate,well) %>%
  distinct()

target_ids <-target_gene_list %>%
  filter(gene_symbol %in% targets) %>%
  filter(!grepl("CTRL",targetid)) %>%
  pull(targetid)


bulk_Tlk_interactions <- interactions_stats_all_feats_df_18112019 %>% 
  filter(query_name =="Rho1", targetid %in% target_ids) %>% 
  left_join(target_gene_list,by = "targetid") %>%
  dplyr::select(query_name,target_gene=gene_symbol.y,feature,mpi,fdr,pval)

myorder<-sc_Tlk_interactions_unfiltered$target_name %>% unique %>% sort



```

# plotting

```{r vizualization}
joint_data <- bulk_Tlk_interactions %>% 
  mutate(type="morphology") %>% 
  rbind(
    sc_Tlk_interactions_unfiltered %>% 
      unite(feature,context,group) %>% 
      dplyr::select(query_name,target_gene=target_name,feature,mpi,fdr,pval=p_value) %>% 
      mutate(type="cell state")
  )

p<- joint_data %>%
  filter( target_gene %in% c("geminin","aurB","osa","polo")) %>%
  ggplot(aes(x=feature,y=factor(target_gene,levels = myorder,ordered = T),size=-log10(pval),col=mpi)) +
    geom_point() +
    scale_color_gradient2(low=google_blue,high = google_yellow) + 
    theme_b110()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    scale_size_area() +
    xlab("Cell Morphology")+
    ylab("Target gene")+
    theme(legend.position = "right") +
    facet_wrap(~type,scales = "free_x")

ggsave("direct_morphinteraction_state_comparison_Rho1_cell_cycle.png",p,width = 12,height = 5)
ggsave("direct_morphinteraction_state_comparison_Rho1_cell_cycle.pdf",p,width = 12,height = 5)

print(p)
```


## Figure 4G State specific interactions of Rab1
# data wrangling

```{r interaction_filtering}

sc_Tlk_interactions_sig <- 
  results_data %>% 
  filter(query_name == "Rab1",fdr<0.1,target_name %in% c("AP-2mu","AP-2sigma","AP-1-2beta") ) %>% 
  as_tibble()

targets<-sc_Tlk_interactions_sig %>% pull(target_name) %>% unique()


sc_Tlk_interactions_unfiltered <- 
  results_data %>% 
  filter(query_name == "Rab1",target_name %in% targets) %>% 
  as_tibble()


target_gene_list<- updated_target_genes %>% 
  as_tibble() %>%
  dplyr::select(plate,well,gene_symbol,hd3gene) %>%
  mutate(well=gsub("^(\\w)0(\\d)$","\\1\\2",well)) %>%
  unite("targetid",plate,well) %>%
  distinct()

target_ids <-target_gene_list %>%
  filter(gene_symbol %in% targets) %>%
  filter(!grepl("CTRL",targetid)) %>%
  pull(targetid)


bulk_Tlk_interactions <- interactions_stats_all_feats_df_18112019 %>% 
  filter(query_name =="Rab1", targetid %in% target_ids) %>% 
  left_join(target_gene_list,by = "targetid") %>%
  dplyr::select(query_name,target_gene=gene_symbol.y,feature,mpi,fdr,pval)

myorder<-sc_Tlk_interactions_unfiltered$target_name %>% unique %>% sort



```

# plotting

```{r vizualization}

joint_data <- bulk_Tlk_interactions %>% 
  mutate(type="morphology") %>% 
  rbind(
    sc_Tlk_interactions_unfiltered %>% 
      unite(feature,context,group) %>% 
      dplyr::select(query_name,target_gene=target_name,feature,mpi,fdr,pval=p_value) %>% 
      mutate(type="cell state")
  )

p <- joint_data %>% 
  filter( target_gene %in% c("AP-2mu","AP-2sigma","AP-1-2beta")) %>%
  ggplot(aes(x=feature,y=factor(target_gene,levels = myorder,ordered = T),size=-log10(pval),col=mpi)) +
    geom_point() +
    scale_color_gradient2(low=google_blue,high = google_yellow) +
    theme_b110()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    scale_size_area() +
    xlab("Cell Morphology")+
    ylab("Target gene")+
    theme(legend.position = "right") +
    facet_wrap(~type,scales = "free_x")

ggsave("direct_morphinteraction_state_comparison_Rab1_APcomplx.png",p,width = 12,height = 5)
ggsave("direct_morphinteraction_state_comparison_Rab1_APcomplx.pdf",p,width = 12,height = 5)

print(p)
```
