---
title: "0-preprocessing-featureselection"
author: "Florian Heigwer"
date: "12/07/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(patchwork)
library(ggrepel)
library(GGally)
library(MASS)
library(ggridges)
library(cowplot)
library("dendextend")
library(dtplyr)
library(corrr)
library(RColorBrewer)
library(ggrastr)
theme_set(theme_cowplot())
```

# use the filtered data data frame to assess feature reporducibility and redundancy

```{r, eval=FALSE}

f<-function(x){
    y <- x %>% spread(screen,value) 
    return(cor(y[,4:5],use = "p",method = "p")[2])
}

 l=list()
 
 for(i in list.files("../../SYNGENE_interactions/raw_data/",pattern = "^filtered_data*")){
    print(i)
    load(paste0("../../SYNGENE_interactions/raw_data/",i))
    l[[i]]<- filtered_data%>% 
            dplyr::select(gene_id,design,value,query_name,screen) %>%
            group_by(query_name) %>% 
            do(c= f(.)) %>% 
            unnest()
 }
 
filtered_data_cor_many_feats<-bind_rows(l,.id="feature") %>% mutate(feature=gsub(feature,pattern = "filtered_data_(.*).RData",replacement = "\\1"))
  
saveRDS(filtered_data_cor_many_feats,file = "../../SYNGENE_interactions/raw_data/cor_many_feats_18112019.rds")

```

#get the reproducible feature

Filter only for those features who median pearson correlation coefficient if higher the 0.4 over 98 duplicated screens

```{r}
if(!exists("filtered_data_cor_many_feats")){
  filtered_data_cor_many_feats<-readRDS("../../SYNGENE_interactions/raw_data/cor_many_feats_18112019.rds")
}

reproducible_feature<-filtered_data_cor_many_feats %>%
    group_by(feature) %>%
    summarise(c=median(c,na.rm = T)) %>%
    filter(c>0.4) %>%
    pull(feature) %>%
    unique() 

saveRDS(reproducible_feature,"processed_data/reproducible_feature_18112019.rds")
```


#create dataframe of all normalized data for reproducible feature

we do this in order to use carets findCorrelation function to filter out redundant features

```{r, eval=FALSE}
l=list()

for(i in list.files("../../SYNGENE_interactions/raw_data/",pattern = "^filtered_data*")){
 
  if(gsub(i,pattern = "filtered_data_(.*).RData",replacement = "\\1") %in% reproducible_feature){
    print(i)
    load(paste0("../../SYNGENE_interactions/raw_data/",i))
    l[[i]]=filtered_data
  }
  
}

filtered_data_many_feats<-bind_rows(l,.id="feature") %>% mutate(feature=gsub(feature,pattern = "filtered_data_(.*).RData",replacement = "\\1"))
saveRDS(filtered_data_many_feats,file = "../../SYNGENE_interactions/raw_data/collected_filtered_data_many_feats_18112019.rds")

```


#Find the non redundant features

We use the reporducible features to start with and their values over all screens averaged to find co-variate features and exclude them

```{r}
if(!exists("filtered_data_many_feats")){
  filtered_data_many_feats <- readRDS("../../SYNGENE_interactions/raw_data/collected_filtered_data_many_feats_18112019.rds")
}

filtered_data_many_feats_dt <- filtered_data_many_feats %>% group_by(targetid,query_name,feature) %>% summarise(value=mean(value,na.rm=TRUE)) %>% spread(feature,value) 

saveRDS(filtered_data_many_feats_dt,"../../SYNGENE_interactions/raw_data/collected_filtered_data_many_feats_dt_18112019.rds")

if(!exists("filtered_data_many_feats_dt")){
  filtered_data_many_feats_dt <- readRDS("../../SYNGENE_interactions/raw_data/collected_filtered_data_many_feats_dt_18112019.rds")
}

cor_matrix<-filtered_data_many_feats_dt %>% .[,reproducible_feature_sorted] %>% correlate(method="p",use="p")

corm<-cor_matrix %>% select_if(is.numeric)
rownames(corm) <- cor_matrix$rowname
corm<-as.matrix(corm)

redundant_features<-caret::findCorrelation(corm,cutoff = 0.7)

usable_features<-c("cells",reproducible_feature[-redundant_features])

saveRDS(usable_features,"processed_data/usable_features_18112019.rds")
```
