---
title: "cons_functional_groups_fly_features"
author: "Vera"
date: "03/02/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## In this Markdown, I look at the iteraction profile correlations for the fly, the first one calculated based on cell count, the second calculated based on features

Let's see if there are any differences 

## 1. Load Packages

```{r}

library(tidyverse)
library(dplyr)
library(ggplot2)
#library(VennDiagram)
#library(ggsignif)

```

## 2. Load data

```{r}

# load complex annotations table (fly) - copied from Maria's folder
fly_complex_annotations <- read_delim("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/complex_annotations(1).txt", delim = "\t") %>% 
  rename(Gene_name = genes)

# Genetic interaction profile similarity values for Fly (based on cell count), (Florian, 29.01.2020):
load(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/cell_count_interaction_correlations_pearson_p_unfiltered_fly.RData")
# this file is named GI_corrs

# Genetic interaction profile similarity values for Fly (based on cell count), (Florian, 03.02.2020):
load(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/feature_correlations_pearson_p_unfiltered_fly.RData")
# this file is named feature_corrs

```

## 3. Tidy up the data

```{r}

# use FLorian's code to separate gene and IDs into single columns:
# for cell count-based data:
fly_correlation_cellcount <- GI_corrs %>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,idx,idy,r) 
dim(fly_correlation_cellcount)
# [1] 23526370        5
# for feature-based data:
fly_correlation_features <- feature_corrs %>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,idx,idy,r) 
dim(fly_correlation_features)
# [1] 23526370        5

# some of the correlations correspond to wells without dsRNA or with only one dsRNA?
# in those columns, the gene is marked with "-" -> I'm gonna filter out lines in which genex or geney equals "-"
fly_correlation_cellcount <- fly_correlation_cellcount %>% 
  filter(genex != "-", geney != "-")
dim(fly_correlation_cellcount)
# [1] 23498940        5
fly_correlation_features <- fly_correlation_features %>% 
  filter(genex != "-", geney != "-")
dim(fly_correlation_features)
# [1] 23498940        5

# Since I am only comparing fly data here (no yeast data), I do not have to filter the genes with regard to whether they are present in the orthologues list

# I have to filter the genes with regard to whether they have a complex annotation:
fly_correlation_cellcount_anno <- fly_correlation_cellcount %>% 
  filter(genex %in% fly_complex_annotations$Gene_name & geney %in% fly_complex_annotations$Gene_name)
dim(fly_correlation_cellcount_anno)
# [1] 70125     5
fly_correlation_features_anno <- fly_correlation_features %>% 
  filter(genex %in% fly_complex_annotations$Gene_name & geney %in% fly_complex_annotations$Gene_name)
dim(fly_correlation_features_anno)
# [1] 70125     5

# Create new columns in those two datasets (complex_1 and complex_2), by left-joining with the annotations list and add column "type"
# cell count-based data:
fly_correlation_cellcount_anno <- fly_correlation_cellcount_anno %>% 
  rename(Gene_name = genex) %>% 
  left_join(fly_complex_annotations, by = "Gene_name") %>%
  rename(Gene_1 = Gene_name, Complex_1 = complex) %>% 
  rename(Gene_name = geney) %>% 
  left_join(fly_complex_annotations, by = "Gene_name") %>% 
  rename(Gene_2 = Gene_name, Complex_2 = complex) %>% 
  mutate(type = ifelse(Complex_1 == Complex_2, "internal", "external"))

# feature-based data:
fly_correlation_features_anno <- fly_correlation_features_anno %>% 
  rename(Gene_name = genex) %>% 
  left_join(fly_complex_annotations, by = "Gene_name") %>%
  rename(Gene_1 = Gene_name, Complex_1 = complex) %>% 
  rename(Gene_name = geney) %>% 
  left_join(fly_complex_annotations, by = "Gene_name") %>% 
  rename(Gene_2 = Gene_name, Complex_2 = complex) %>% 
  mutate(type = ifelse(Complex_1 == Complex_2, "internal", "external"))

# Let's see if the columns for genes and complexes in the two dataframes are identical, so I could create a common dataframe with both r values
identical(fly_correlation_cellcount_anno$Gene_1, fly_correlation_features_anno$Gene_1)
identical(fly_correlation_cellcount_anno$Gene_2, fly_correlation_features_anno$Gene_2)
identical(fly_correlation_cellcount_anno$Complex_1, fly_correlation_features_anno$Complex_1)
identical(fly_correlation_cellcount_anno$Complex_2, fly_correlation_features_anno$Complex_2)
identical(fly_correlation_cellcount_anno$type, fly_correlation_features_anno$type)
# returs TRUE for all of them 

# create common dataframe
fly_correlation_common_anno <- fly_correlation_cellcount_anno %>% 
  rename(r_cellcount = r) %>%                                                               # needed to avoid columns with the same name
  select(-Complex_1, -Complex_2, -type) %>%                                                 # I don't need those (they are identical to the features dataframe)
  left_join(fly_correlation_features_anno, by = c("Gene_1", "Gene_2", "idx", "idy")) %>%    # combine both tables (all four columns are needed in "by" to avoid duplications)
  select(-idx, -idy) %>%                                                                    # Now I don't need the IDs anymore I think
  rename(r_features = r) %>%                                                                # rename the second r column to clarify which belongs to which dataset
  select(Gene_1, Gene_2, Complex_1, Complex_2, type, r_cellcount, r_features)               # re-order the columns
dim(fly_correlation_common_anno)
# [1] 70125     7               # same number of rows as the original dataframes
dim(fly_correlation_common_anno %>%  distinct())
# [1] 70125     7               # no duplications

# create another common dataframe with bind rows to be able to use "fill = based_on" later
fly_correlation_common_anno_rows <- bind_rows(fly_correlation_cellcount_anno, fly_correlation_features_anno, .id = "based_on") %>% 
  mutate(based_on = ifelse(based_on == 1, "cell count", "features")) 

```

# 4. Plot Density Histograms of correlation values: differences between two approaches?

```{r}

ggplot(fly_correlation_common_anno, aes(x = r_cellcount)) +
  theme_bw() +
  geom_histogram(binwidth = 0.001, color = "slateblue1") +
  xlab("pearson correlation") +
  geom_vline(xintercept = 0, color = "red") +
  ggtitle(" Density histogram of pearson correlation values, fly, \n calculated based on cell count")
ggsave("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/density_fly_cellcount.png")
  
ggplot(fly_correlation_common_anno, aes(x = r_features)) +
  theme_bw() +
  geom_histogram(binwidth = 0.001, color = "cadetblue3") +
  xlab("pearson correlation") +
  geom_vline(xintercept = 0, color = "red") +
  ggtitle(" Density histogram of pearson correlation values, fly, \n calculated based on features")
ggsave("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/density_fly_features.png")

# create dataframe with bind rows to be able to use "fill = based_on" later
fly_correlation_common_anno_rows <- bind_rows(fly_correlation_cellcount_anno, fly_correlation_features_anno, .id = "based_on") %>% 
  mutate(based_on = ifelse(based_on == 1, "cell count", "features")) 

# plot common density plot
ggplot(fly_correlation_common_anno_rows) +
  theme_bw() +
  geom_density(aes(x = r, fill = based_on), alpha = 0.4) +
  scale_fill_manual(values = c("blue3", "lightblue")) +
  xlab("r value") +
  ggtitle("Distribution of similarity values in fly: calculated by cell count vs. features") +
  guides(fill = guide_legend(title = c("Based on")))

# plot common histogram
ggplot(fly_correlation_common_anno_rows) +
  theme_bw() +
  geom_histogram(binwidth = 0.001, aes(x = r, fill = based_on), alpha = 0.4) +
  scale_fill_manual(values = c("blue3", "lightblue")) +
  xlab("r value") +
  ggtitle("Distribution of similarity values in fly: calculated by cell count vs. features") +
  guides(fill = guide_legend(title = c("Based on")))

```

## 5. Which complexes? How many gene members per complex?

```{r}

# How many different complexes?
nrow(fly_correlation_common_anno %>% select(Complex_1) %>% distinct())
# 32
nrow(fly_correlation_common_anno %>% select(Complex_2) %>% distinct())
# 32

fly_complex_annotations %>% 
  group_by(complex) %>% 
  filter(n() >= 4) %>% 
  count() %>% 
  view()

# check if the annotated complexes have at least 4 gene members in the dataset
fly_correlation_common_anno %>% 
  select(Gene_1, Complex_1) %>% 
  distinct() %>% 
  group_by(Complex_1) %>% 
  count()
# there are some complexes which have less then 4 gene members

# create dataframes (for complex_1 and complex_2 containing only complexes with >= 4 gene members)
C1_n4 <- fly_correlation_common_anno %>% 
  select(Gene_1, Complex_1) %>% 
  distinct() %>% 
  group_by(Complex_1) %>% 
  filter(n() >=4) %>% 
  count()
C2_n4 <- fly_correlation_common_anno %>% 
  select(Gene_2, Complex_2) %>% 
  distinct() %>% 
  group_by(Complex_2) %>% 
  filter(n() >=4) %>% 
  count()
identical(C1_n4$Complex_1, C2_n4$Complex_2)
# TRUE

# filter datasets for complexes with >=4 gene members:
fly_correlation_common_anno_n4 <- fly_correlation_common_anno %>% 
  filter(Complex_1 %in% C1_n4$Complex_1 & Complex_2 %in% C1_n4$Complex_1)
nrow(fly_correlation_common_anno_n4)
# [1] 66066
# How many complexes are left?
nrow(fly_correlation_common_anno_n4 %>% select(Complex_1) %>% unique())
# 27

fly_correlation_common_anno_rows_n4 <- fly_correlation_common_anno_rows %>% 
  filter(Complex_1 %in% C1_n4$Complex_1 & Complex_2 %in% C1_n4$Complex_1)

# which complexes are those 27?
print((fly_correlation_common_anno_n4 %>% select(Complex_1) %>% unique())$Complex_1)
# [1] "BAPPBAP" "TIP60"   "IlR"     "RAS"     "COPI"    "AP"      "APC"     "DYN"     "PATPASE" "OXPHOS"  "IFT"     "TRAPP"   "TFIID"   "VPSC"    "HSP60"   "PROT"  
# [17] "ESCRT"   "COP9"    "IlRNeg"  "IlRPos"  "STAT"    "COMP"    "EXOC"    "RNAPII"  "GATOR"   "MED"     "COPII"  
# create vector
complexes_n4 <- fly_correlation_common_anno_n4 %>% 
  select(Complex_1) %>% 
  unique()
complexes_n4_vec <- complexes_n4[["Complex_1"]]

```

# 6. Plot Density Histograms of correlation values: differences between two approaches?

```{r}

ggplot(fly_correlation_common_anno_n4, aes(x = r_cellcount)) +
  theme_bw() +
  geom_histogram(binwidth = 0.001, color = "slateblue1") +
  xlab("similarity value") +
  geom_vline(xintercept = 0, color = "red")
  
ggplot(fly_correlation_common_anno_n4, aes(x = r_features)) +
  theme_bw() +
  geom_histogram(binwidth = 0.001, color = "cadetblue3") +
  xlab("similarity value") +
  geom_vline(xintercept = 0, color = "red")

# plot common density plot
ggplot(fly_correlation_common_anno_rows_n4) +
  theme_bw() +
  geom_density(aes(x = r, fill = based_on), alpha = 0.4) +
  scale_fill_manual(values = c("slateblue1", "cadetblue3")) +
  xlab("r value") +
  ggtitle("Distribution of similarity values in fly: calculated based on cell count/features") +
  guides(fill = guide_legend(title = c("Based on")))

# plot common histogram
ggplot(fly_correlation_common_anno_rows_n4) +
  theme_bw() +
  geom_histogram(binwidth = 0.001, aes(x = r, fill = based_on), alpha = 0.4) +
  scale_fill_manual(values = c("slateblue1", "cadetblue3")) +
  xlab("r value") +
  ggtitle("Distribution of similarity values in fly: calculated based on cell count/features") +
  guides(fill = guide_legend(title = c("Based on")))

```

## 7. Calculate p-values for density shifts internal vs. external (will be plotted in next chunk)

```{r}

tt_cellcount <- data.frame(matrix(ncol = 3, nrow = length(complexes_n4_vec))) %>% 
  rename(based_on = X1, complex = X2, pval = X3)
tt_features <- data.frame(matrix(ncol = 3, nrow = length(complexes_n4_vec))) %>% 
  rename(based_on = X1, complex = X2, pval = X3)

j <- 1
for (i in (complexes_n4_vec)) {
    tt_cellcount$based_on[j] <- "cell count"  
    tt_cellcount$complex[j] <- as.character(i)
    tt_cellcount$pval[j] <- t.test(formula = r ~type, alternative = c("two.sided"), data = fly_correlation_common_anno_rows_n4 %>%  filter((Complex_1 == i | Complex_2 == i), based_on=="cell count"))$p.value
    j <- j+1
}     

j <- 1
for (i in (complexes_n4_vec)) {
    tt_features$based_on[j] <- "features"  
    tt_features$complex[j] <- as.character(i)
    tt_features$pval[j] <- t.test(formula = r ~type, alternative = c("two.sided"), data = fly_correlation_common_anno_rows_n4 %>%  filter((Complex_1 == i | Complex_2 == i), based_on=="features"))$p.value
    j <- j+1
}  

# combine both dataframes in one: 
tt <- as_tibble(bind_rows(tt_cellcount, tt_features)) %>% 
  mutate(pvalround = ifelse(pval < 0.00001, "< 0.00001", as.character(paste0 ("= ",round(pval, digits = 5)))))  # round pvalue/set to < x, to make display easier

```

## 8. Plot Density shift internal vs. external, compare r values based on cell count vs. based on features

```{r}

# For data based on cell count:
for (i in (complexes_n4_vec)) {
plt <- fly_correlation_common_anno_rows_n4 %>% 
  filter(based_on == "cell count") %>% 
  filter(Complex_1 == i | Complex_2 == i) %>% 
  ggplot(aes(x = as.numeric(r), fill = type)) +
    geom_density(alpha = 0.3) +
    scale_fill_manual(values = c("grey", "slateblue1")) +
    theme_classic(base_size = 15) +
    xlab("pearson correlation") +
    ylab("count") +
    geom_vline(xintercept = 0, color = "black", linetype ="dashed") +
    scale_y_continuous(expand = c(0,0)) +
    ggtitle(paste0(" Distribution of pearson correlations, complex ", as.character(i), ", \n fly (based on cell count)"))

plt +
    geom_text(aes(label = paste0("p ", (tt %>%  filter(complex == i, based_on == "cell count"))$pvalround)), x = -layer_scales(plt)$x$range$range[2]+(layer_scales(plt)$x$range$range[2]/1.8), y = layer_scales(plt)$y$range$range[2]-layer_scales(plt)$y$range$range[2]/20, size = 5)
 
ggsave(paste0("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/Plots/density_fly_cellcount_", i, ".png"))
}

# did not work for APC
plt <- fly_correlation_common_anno_rows_n4 %>% 
  filter(based_on == "cell count") %>% 
  filter(Complex_1 == "APC" | Complex_2 == "APC") %>% 
  ggplot(aes(x = as.numeric(r), fill = type)) +
    geom_density(alpha = 0.3) +
    scale_fill_manual(values = c("grey", "slateblue1")) +
    theme_classic(base_size = 15) +
    xlab("pearson correlation") +
    ylab("count") +
    geom_vline(xintercept = 0, color = "black", linetype ="dashed") +
    scale_y_continuous(expand = c(0,0)) +
    ggtitle(" Distribution of pearson correlations, complex APC, \n fly (based on cell count)")
plt +
    geom_text(aes(label = paste0("p ", (tt %>%  filter(complex == "APC", based_on == "cell count"))$pvalround)), x = -layer_scales(plt)$x$range$range[2]+(layer_scales(plt)$x$range$range[2]/1.48), y = layer_scales(plt)$y$range$range[2]-layer_scales(plt)$y$range$range[2]/10, size = 5)
ggsave("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/Plots/density_fly_cellcount_APC.png")

# For data based on features:
for (i in (complexes_n4_vec)) {
plt <- fly_correlation_common_anno_rows_n4 %>% 
  filter(based_on == "features") %>% 
  filter(Complex_1 == i | Complex_2 == i) %>% 
  ggplot(aes(x = as.numeric(r), fill = type)) +
    geom_density(alpha = 0.3) +
    scale_fill_manual(values = c("grey", "cadetblue3")) +
    theme_classic(base_size = 15) +
    xlab("pearson correlation") +
    ylab("count") +
    geom_vline(xintercept = 0, color = "black", linetype ="dashed") +
    scale_y_continuous(expand = c(0,0)) +
    ggtitle(paste0(" Distribution of pearson correlations, complex ", as.character(i), ", \n fly (based on morphological features)"))

plt +
    geom_text(aes(label = paste0("p ", (tt %>%  filter(complex == i, based_on == "features"))$pvalround)), x = layer_scales(plt)$x$range$range[2]-(layer_scales(plt)$x$range$range[2]*1.7), y = layer_scales(plt)$y$range$range[2]-layer_scales(plt)$y$range$range[2]/20, size = 5)
 
ggsave(paste0("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/Plots/density_fly_features_", i, ".png"))
}

```



