---
title: "cons_functional_groups_human"
author: "Vera"
date: "03/02/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## In this markdown, I'll see what I can learn about genetic interaction profiles, clusters, correlations, etc. in the human dataset

## 1. Load packages

```{r}

library(tidyverse)
library(dplyr)
library(ggplot2)

```

## 2. Load data

```{r}

# load human dataset 
# ! only load first time, after this, use the separated columns
# load(file = "/Users/b110/Desktop/VeraPeters/source_data/Achilles_gene_effect_correlations_p_p.RData")
# this tibble is called "ceres_corrs"
# instead: load dataset filtered for genes in the orthologues list (created in chunk 4):
ceres_corrs_sep_in_ortho <- read_csv(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_sep_filtered.csv")

# Load list of orthologue pairs from Ensembl database -27.11.2019
orthologues <- read_delim("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/new_orthologues_list_copy.txt",delim = "\t")
# load complex annotations table (fly) - copied from Maria's folder
fly_complex_annotations <- read_delim("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/complex_annotations(1).txt", delim = "\t") %>% 
  rename(Gene_name = genes)

```

## 3. Inspect human dataset and separate columns 

```{r}

head(ceres_corrs)
#A tibble: 6 x 3
#  x        y                      r
#  <chr>    <chr>              <dbl>
#1 A1BG (1) A1CF (29974)     -0.0866
#2 A1BG (1) A2M (2)           0.0894
#3 A1BG (1) A2ML1 (144568)   -0.0254
#4 A1BG (1) A3GALT2 (127550)  0.0411
#5 A1BG (1) A4GALT (53947)    0.0502
#6 A1BG (1) A4GNT (51146)     0.0547

# in the columns for the gene names, there are additional numbers written behind the gene names

dim(ceres_corrs)
# [1] 168040278         3
# so, apparently everything I am gonna do with this dataset is gonna take forever, because we have 168 million rows (update: no, it's crashing R...)

# let's check for duplicates
# nrow(ceres_corrs %>% distinct())
# [1] 168040278

# write three separate csv files for each column:
write_csv(ceres_corrs[,1], path ="/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_1.csv")
write_csv(ceres_corrs[,2], path ="/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_2.csv")
write_csv(ceres_corrs[,3], path ="/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_3.csv")

### ! after that: restart R, because it is a little weird (or at least empty the environment) ! ###

# next step: load the 1-column files separately, and separate the column into gene and the number:

# column x:
ceres_corrs_1 <- read_csv(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_1.csv")
ceres_corrs_1 <- ceres_corrs_1 %>% separate(x, into = c("x", "xnum"), sep = " ")

head(ceres_corrs_1)
# A tibble: 6 x 2
#  x     xnum 
#  <chr> <chr>
#1 A1BG  (1)  
#2 A1BG  (1)  
#3 A1BG  (1)  
#4 A1BG  (1)  
#5 A1BG  (1)  
#6 A1BG  (1)  
# this seems to have worked.

### ! now, delete the ceres_corrs_1.csv in the folder (and empty trash) ! ###

# and save the new one with separated columns:
write_csv(ceres_corrs_1, path ="/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_1.csv")

### ! restart R, because reading in the next file did not work with only emtpying the environment ! ###

# column y:
ceres_corrs_2 <- read_csv(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_2.csv")
ceres_corrs_2 <- ceres_corrs_2 %>% separate(y, into = c("y", "ynum"), sep = " ")
head(ceres_corrs_2)
# A tibble: 6 x 2
#  y       ynum    
#  <chr>   <chr>   
#1 A1CF    (29974) 
#2 A2M     (2)     
#3 A2ML1   (144568)
#4 A3GALT2 (127550)
#5 A4GALT  (53947) 
#6 A4GNT   (51146) 

### ! now, delete the ceres_corrs_2.csv in the folder (and empty trash) ! ###

# and save the new one with separated columns:
write_csv(ceres_corrs_2, path ="/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_2.csv")

### ! restart R ! ###

# now, I have to read in my three seperated ceres_corrs data files
ceres_corrs_1 <- read_csv(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_1.csv")
ceres_corrs_2 <- read_csv(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_2.csv")
ceres_corrs_3 <- read_csv(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_3.csv")

# combine the three datasets into one:
ceres_corrs_sep <- cbind(ceres_corrs_1, ceres_corrs_2)
ceres_corrs_sep <- cbind(ceres_corrs_sep, ceres_corrs_3)
head(ceres_corrs_sep)
#x xnum       y     ynum           r
#1 A1BG  (1)    A1CF  (29974) -0.08659597
#2 A1BG  (1)     A2M      (2)  0.08942455
#3 A1BG  (1)   A2ML1 (144568) -0.02540437
#4 A1BG  (1) A3GALT2 (127550)  0.04106368
#5 A1BG  (1)  A4GALT  (53947)  0.05020788
#6 A1BG  (1)   A4GNT  (51146)  0.05472507
typeof(ceres_corrs_sep)
# list
# save this as a file:
write_csv(ceres_corrs_sep, path = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_sep_unfiltered.csv")
# note: this file was copied to Sergi's harddrive

# remove single data frames to save space
rm(ceres_corrs_1)
rm(ceres_corrs_2)
rm(ceres_corrs_3)

```

## 4. Filter dataset for genes present in the orthologues list

```{r}

# create vector with human gene names in the orthologues list:
orthologues_human_genes <- orthologues %>%  select(Human_gene_name) %>%  drop_na()
orthologues_human_genes_vec <- orthologues_human_genes[["Human_gene_name"]]
length(orthologues_human_genes_vec)
# [1] 37087

# filter ceres_corrs_sep for genes in the orthologues list:
ceres_corrs_sep_in_ortho <- ceres_corrs_sep %>% filter(x %in% orthologues_human_genes_vec)
dim(ceres_corrs_sep_in_ortho)
# [1] 78199289        5
ceres_corrs_sep_in_ortho <- ceres_corrs_sep_in_ortho %>% filter(y %in% orthologues_human_genes_vec)
dim(ceres_corrs_sep_in_ortho)
# [1] 37208251        5
# save this in a new file as well:
write_csv(ceres_corrs_sep_in_ortho, path = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_sep_filtered.csv")



### ! restart R ! ###

# load saved file:
ceres_corrs_sep_in_ortho <- read_csv(file = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_sep_filtered.csv")

# let's see if there are any duplicates when not considering the weird gene numbers, but only the gene names:
nrow(ceres_corrs_sep_in_ortho)
# [1] 37208251
nrow(ceres_corrs_sep_in_ortho %>%  select(x, y) %>% distinct())
# [1] 37208251
# apparently, the weird numbers do not add any useful information, there gene name-pairs by themselves are unique
# meaning I can drop the columns with the weird numbers:
ceres_corrs_sep_in_ortho_wonum <- ceres_corrs_sep_in_ortho %>% select(-xnum, -ynum)
# save this one in a new file as well:
write_csv(ceres_corrs_sep_in_ortho_wonum, path = "/Users/b110/Desktop/VeraPeters/conserved_functional_groups/ceres_corrs_sep_filtered_wonum.csv")
# remove object with 5 variables:
rm(ceres_corrs_sep_in_ortho)

```

## 5. Add complex columns and type (internal/external) to dataset

```{r}

orthologues_annotations <- inner_join(orthologues, fly_complex_annotations, by = "Gene_name")

# filter dataset: keep only rows, in which both gene names have annotations:
ceres_corrs_sep_in_ortho_anno <- ceres_corrs_sep_in_ortho_wonum %>% 
  filter(x %in% orthologues_annotations$Human_gene_name) %>% 
  filter(y %in% orthologues_annotations$Human_gene_name)
dim(ceres_corrs_sep_in_ortho_anno)
# [1] 173166      3

# add columns complex_x and complex_y, and type:
orthologues_annotations_human <- orthologues_annotations %>% select(Human_gene_name, complex)

ceres_corrs_sep_in_ortho_anno <- ceres_corrs_sep_in_ortho_anno %>%            
  rename(Human_gene_name = x) %>%                                             # rename to enable join by
  left_join(orthologues_annotations_human, by = "Human_gene_name") %>%        # join with complex annotations for first gene
  rename(Gene_1 = Human_gene_name, Complex_1 = complex) %>%                   # rename to avoid duplications 
  rename(Human_gene_name = y) %>%                                             # rename to enable join by
  left_join(orthologues_annotations_human, by = "Human_gene_name") %>%        # join with complex annotations for second gene
  rename(Gene_2 = Human_gene_name, Complex_2 = complex) %>%                   # rename to naming consistent
  mutate(type = ifelse(Complex_1 == Complex_2, "internal", "external"))       # add column "type" to specify internal vs. external

head(ceres_corrs_sep_in_ortho_anno)
# A tibble: 6 x 6
#  Gene_1 Gene_2       r Complex_1 Complex_2 type    
#  <chr>  <chr>    <dbl> <chr>     <chr>     <chr>   
#1 ACTR10 ACTR1A  0.201  DYN       DYN       internal
#2 ACTR10 ACTR2   0.0213 DYN       ARPC      external
#3 ACTR10 ACTR3   0.160  DYN       ARPC      external
#4 ACTR10 ADRM1  -0.0523 DYN       PROT      external
#5 ACTR10 ADRM1  -0.0523 DYN       PROT      external
#6 ACTR10 ANAPC1  0.141  DYN       APC       external
dim(ceres_corrs_sep_in_ortho_anno)
# [1] 345900      6

# Problem:
nrow(ceres_corrs_sep_in_ortho_anno)
# [1] 345900
nrow(ceres_corrs_sep_in_ortho_anno %>% select(Gene_1, Gene_2, r) %>% distinct())
# [1] 173166
# apparently, there are genes which correspond to multiple fly genes which are annotated with different complexes?

# let's check this in the orthologues list:
nrow(orthologues_annotations %>%  select(Human_gene_name, Gene_name, complex) %>% distinct())
# [1] 862
nrow(orthologues_annotations %>%  select(Human_gene_name, complex) %>% distinct())
# [1] 678
nrow(orthologues_annotations_human)
# [1] 1020
nrow(orthologues_annotations_human %>%  select(Human_gene_name) %>% distinct())
# [1] 659

####

# to avoid this, I'll choose to keep only the fly gene/complex annotation in the list, for which the percentage identity is highest
# create new "human sub-dataframe" of orthologues list
orthologues_annotations_human <- orthologues_annotations %>% 
  select(Human_gene_name, Human_orthology_confidence_0low_1high, percentage_id_query_gene_identical_to_target_Human_gene, Gene_name, complex) %>% 
  drop_na()

orthologues_annotations_human <- orthologues_annotations_human %>% 
  group_by(Human_gene_name) %>% 
  arrange(desc(percentage_id_query_gene_identical_to_target_Human_gene)) %>%    # arrange percentage identical values (decreasing)
  do(head(.,1)) %>%                                                             # keep only the row with the highest percentage identical value
  ungroup()
nrow(orthologues_annotations_human)
# [1] 658 (one less than I want?)

####

# repeat steps from before, but with new orthologues_annotations_human list:
ceres_corrs_sep_in_ortho_anno <- ceres_corrs_sep_in_ortho_wonum %>% 
  filter(x %in% orthologues_annotations$Human_gene_name) %>% 
  filter(y %in% orthologues_annotations$Human_gene_name)
dim(ceres_corrs_sep_in_ortho_anno)

# add columns complex_x and complex_y, and type:
ceres_corrs_sep_in_ortho_anno <- ceres_corrs_sep_in_ortho_anno %>%            
  rename(Human_gene_name = x) %>%                                                                                     # rename to enable join by
  left_join((orthologues_annotations_human %>% select(Human_gene_name, complex)), by = "Human_gene_name") %>%         # join with complex annotations for first gene
  rename(Gene_1 = Human_gene_name, Complex_1 = complex) %>%                                                           # rename to avoid duplications 
  rename(Human_gene_name = y) %>%                                                                                     # rename to enable join by
  left_join((orthologues_annotations_human %>% select(Human_gene_name, complex)), by = "Human_gene_name") %>%         # join with complex annotations for second gene
  rename(Gene_2 = Human_gene_name, Complex_2 = complex) %>%                                                           # rename to naming consistent
  mutate(type = ifelse(Complex_1 == Complex_2, "internal", "external"))                                               # add column "type" to specify internal vs. external
dim(ceres_corrs_sep_in_ortho_anno)
# [1] 173166      6

```

## 6. Examine complexes and filter for complexes with >= 4 gene members

```{r}

# how many different complexes do we have?
nrow(ceres_corrs_sep_in_ortho_anno %>% select(Complex_1) %>% unique())
# [1] 32
nrow(ceres_corrs_sep_in_ortho_anno %>% select(Complex_2) %>% unique())
# [1] 32
# do we have the same complexes in Complex_1 and Complex_2? 
identical((ceres_corrs_sep_in_ortho_anno %>% select(Complex_1) %>% unique())$Complex_1,(ceres_corrs_sep_in_ortho_anno %>% select(Complex_2) %>% unique())$Complex_2)
# [1] TRUE
# which complexes?
(ceres_corrs_sep_in_ortho_anno %>% select(Complex_1) %>% unique())$Complex_1
#[1] "DYN"      "ARPC"     "PROT"     "APC"      "AP"       "COPI"     "BAPPBAP"  "IFT"      "IlR"      "COMP"     "ELG1C"    "PATPASE"  "OXPHOS"   "TIP60"    "TFIID"   
#[16] "IlRNeg"   "RAS"      "HSP60"    "MED"      "ESCRT"    "CLATHRIN" "COP9"     "IlRPos"   "GATOR"    "EXOC"     "PFDN"     "RNAPII"   "COPII"    "RETRO"    "STAT"    
#[31] "TRAPP"    "VPSC"

C1_n4 <- ceres_corrs_sep_in_ortho_anno %>% 
  select(Gene_1, Complex_1) %>% 
  distinct() %>% 
  group_by(Complex_1) %>% 
  filter(n() >=4) %>% 
  count()
C2_n4 <- ceres_corrs_sep_in_ortho_anno %>% 
  select(Gene_2, Complex_2) %>% 
  distinct() %>% 
  group_by(Complex_2) %>% 
  filter(n() >=4) %>% 
  count()

identical(C1_n4$Complex_1, C2_n4$Complex_2)
# [1] TRUE -> filtering for one of those is sufficient

# filter dataset for complexes with >= 4 gene members:
ceres_corrs_sep_in_ortho_anno_n4 <- ceres_corrs_sep_in_ortho_anno %>% 
  filter(Complex_1 %in% C1_n4$Complex_1 & Complex_2 %in% C1_n4$Complex_1)
dim(ceres_corrs_sep_in_ortho_anno_n4)
# [1] 173166      6

# all the complexes had >= 4 gene members!

# create vector with complex names:
complexes_n4_vec <- C1_n4[["Complex_1"]]

```

## 7. Plot density histogram of correlation values

```{r}

ceres_corrs_sep_in_ortho_anno_n4 %>% 
  ggplot(aes(x = r)) +
  theme_bw() +
  geom_histogram(binwidth = 0.001, color = "darkolivegreen3") +
  xlab("pearson correlation") +
  geom_vline(xintercept = 0, color = "red") +
  ggtitle("Density histogram of pearson correlation values, human")
ggsave(file ="/Users/b110/Desktop/VeraPeters/conserved_functional_groups/Plots/density_human.png")

```

## 8. Calculate p-values for density shifts internal vs. external (will be plotted in next chunk)

```{r}

tt_human <- data.frame(matrix(ncol = 2, nrow = length(complexes_n4_vec))) %>% 
  rename(complex = X1, pval = X2)

j <- 1
for (i in (complexes_n4_vec)) {
    tt_human$complex[j] <- as.character(i)
    tt_human$pval[j] <- t.test(formula = r ~type, alternative = c("two.sided"), data = ceres_corrs_sep_in_ortho_anno_n4 %>%  filter(Complex_1 == i | Complex_2 == i))$p.value
    j <- j+1
}    

tt_human <- tt_human %>% 
  mutate(pvalround = ifelse(pval < 0.00001, "< 0.00001", as.character(paste0 ("= ",round(pval, digits = 5)))))  # round pvalue/set to < x, to make display easier

```

## 9. Plot Density shift internal vs. external

```{r}

# For data based on cell count:
for (i in (complexes_n4_vec)) {
plt <- ceres_corrs_sep_in_ortho_anno_n4 %>% 
  filter(Complex_1 == i | Complex_2 == i) %>% 
  ggplot(aes(x = as.numeric(r), fill = type)) +
    geom_density(alpha = 0.3) +
    scale_fill_manual(values = c("grey", "darkolivegreen3")) +
    theme_classic(base_size = 15) +
    xlab("pearson correlation") +
    ylab("count") +
    geom_vline(xintercept = 0, color = "black", linetype ="dashed") +
    scale_y_continuous(expand = c(0,0)) +
    ggtitle(paste0(" Distribution of pearson correlations, complex ", as.character(i), ", \n human "))

plt +
    geom_text(aes(label = paste0("p ", (tt_human %>%  filter(complex == i))$pvalround)), x = +layer_scales(plt)$x$range$range[2]-(layer_scales(plt)$x$range$range[2]/10), y = layer_scales(plt)$y$range$range[2]-layer_scales(plt)$y$range$range[2]/20, size = 5)
 
ggsave(paste0("/Users/b110/Desktop/VeraPeters/conserved_functional_groups/Plots/density_human_", i, ".png"))
}

```

## 10. Min, Max, Median of correlation values:

```{r}

min(as.numeric(ceres_corrs_sep_in_ortho_anno_n4$r))
# [1] -0.3565629
max(as.numeric(ceres_corrs_sep_in_ortho_anno_n4$r))
# [1] 0.9258851
median(as.numeric(ceres_corrs_sep_in_ortho_anno_n4$r))
# [1] 0.005080773

```








