---
title: "Suppl. Figure 1S1"
author: "Florian Heigwer"
date: "11/19/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(patchwork)
library(ggrepel)
library(GGally)
library(MASS)
library(ggridges)
library(cowplot)
library("dendextend")
library(dtplyr)
library(corrr)
library(RColorBrewer)
library(ggrastr)
theme_set(theme_cowplot())

theme_b110<-function(){
  theme_classic() +
  theme(
    axis.text=element_text(size = 10), 
    axis.title=element_text(size = 10),
    plot.title = element_text(size = 12,hjust = 0.5,face="bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size =10),
    legend.position = "bottom"
    )
}


sgi_blue    = '#5087C8'
sgi_yellow1 = '#F2EE35'
sgi_yellow2 = '#FED98E'
b110_grey   = '#808080'
b110_grey_light   = '#909090'
b110_transparent_black = alpha('#000000',0.5)
google_red='#dd4b39'
google_green='#0F9D58'
google_yellow='#F4B400'
google_blue='#4285F4'

```

## Figure 1S1

```{r}
load("processed_data/statistically_tested_pi_cells.RData")
load("processed_data/filtered_data_cells.RData")
load("processed_data/normalized_data_cells.RData")

feature="nuclear count"

interac_sub<-interaction_stats %>% dplyr::select(gene_symbol,mpi,fdr,fbgn,targetid,target_main,query_main,query_name)

filtered_data_mean<-filtered_data %>% group_by(targetid,query_name) %>% summarise(value=mean(value,na.rm=T))

joined_sub<-filtered_data_mean %>% left_join(interac_sub)
```

## Supplement Figure S1 Outlier removal explanation

  # S1 A-C plot raw data for the raptor screens

```{r}
raptor_data<-feature_wise %>% filter(screen %in% c("S060","S062"),kind=="sample") %>% dplyr::select(-value) %>% spread(screen,rawvalue) %>% dplyr::select(S060,S062)

p1 <- raptor_data %>%
  ggplot(aes(x=S060,y=S062)) + 
  geom_abline(slope = 1,lty=2) +
  geom_vline(xintercept = 0,lty=2) +
  geom_hline(yintercept = 0,lty=2) +
  geom_point(pch=19,col=b110_transparent_black) + 
  geom_smooth(col=b110_grey,method="lm") +
  ylab(paste0(feature," replicate 2")) +
  xlab(paste0(feature," replicate 1")) +
  ggtitle(paste0("raptor ","outlier plot")) +
  scale_color_manual(values = c("normal"=b110_grey_light,"outlier"=sgi_blue))+
  theme_b110()+
  stat_cor()
```

  #plot normalized (score, plate bias, screen bias) data for the raptor screens
  
```{r}
  raptor_data<-feature_wise %>% filter(screen %in% c("S060","S062"),kind=="sample") %>% dplyr::select(-rawvalue) %>% spread(screen,value) %>% dplyr::select(S060,S062)

  mdl<-MASS::rlm(S060~S062,raptor_data) #fit robust linear model for finding regression weights as outlier detection method
  raptor_data$cd<-mdl$w # set the outlier weight as the distance in the normed data data frame, the weight is inverse correlated to the outlierness of a point
```

  #plot normalized data colored by outlierness score
  
```{r}

p2 <- raptor_data %>%
    ggplot(aes(x=S060,y=S062,col=cd)) + 
    geom_abline(slope = 1,lty=2) +
    geom_vline(xintercept = 0,lty=2) +
    geom_hline(yintercept = 0,lty=2) +
    geom_point(pch=19) + 
    geom_smooth(col=b110_grey,method="lm") +
    ylab(paste0(feature," replicate 2")) +
    xlab(paste0(feature," replicate 1")) +
    ggtitle(paste0("raptor ","outlier plot")) +
    theme_b110()+
    stat_cor()
```

  #plot normalized data colored points as outliers if their weight is less than 20 % of the mean outlier weight
  
```{r}
  
p3 <- raptor_data %>%
    mutate(outlier=if_else(cd<1/5*mean(cd,na.rm = T),"outlier","normal")) %>% 
    ggplot(aes(x=S060,y=S062)) + 
    geom_abline(slope = 1,lty=2) +
    geom_vline(xintercept = 0,lty=2) +
    geom_hline(yintercept = 0,lty=2) +
    geom_point(aes(col=outlier)) + 
    geom_smooth(col="black",method="rlm") +
    ylab(paste0(feature," replicate 2")) +
    xlab(paste0(feature," replicate 1")) +
    ggtitle(paste0("raptor ","outlier plot")) +
    theme_b110()+
    scale_color_manual(values = c("normal"=b110_grey_light,"outlier"=sgi_blue))
  

p4 <- p1 + p2 + p3

ggsave("plots/S1_data_norm_outlier_remove.png",width = 24,height = 10,units = "cm")
ggsave("plots/S1_data_norm_outlier_remove.pdf",width = 24,height = 10,units = "cm")
```

## S1 D-G Plot the reproducibility of interactions amongst replicates

```{r}

#for raptor

a <- interaction_stats %>% 
  filter(query_name=="raptor") %>% 
    ggplot(aes(x=(`1`+`4`)/2,y=(`2`+`3`)/2)) +
     geom_abline(slope = 1,lty=2) +
     geom_vline(xintercept = 0,lty=2) +
     geom_hline(yintercept = 0,lty=2) +
     geom_point(col=b110_grey) + 
     geom_smooth(col="black",method="rlm") +
     stat_cor() +
     ylab(paste0(feature," replicate 2 [π]")) +
     xlab(paste0(feature," replicate 1 [π]")) +
     ggtitle(paste0("raptor ","interaction reproducibility")) +
     theme_b110()

#for Tor

b <- interaction_stats %>% 
  filter(query_name=="Tor") %>% 
    ggplot(aes(x=(`1`+`4`)/2,y=(`2`+`3`)/2)) +
     geom_abline(slope = 1,lty=2) +
     geom_vline(xintercept = 0,lty=2) +
     geom_hline(yintercept = 0,lty=2) +
     geom_point(col=b110_grey) + 
     geom_smooth(col="black",method="rlm") +
     stat_cor() +
     ylab(paste0(feature," replicate 2 [π]")) +
     xlab(paste0(feature," replicate 1 [π]")) +
     ggtitle(paste0("Tor ","interaction reproducibility")) +
     theme_b110()

#for E(Pc)

c <- interaction_stats %>% 
  filter(query_name=="E(Pc)") %>% 
    ggplot(aes(x=(`1`+`4`)/2,y=(`2`+`3`)/2)) +
     geom_abline(slope = 1,lty=2) +
     geom_vline(xintercept = 0,lty=2) +
     geom_hline(yintercept = 0,lty=2) +
     geom_point(col=b110_grey) + 
     geom_smooth(col="black",method="rlm") +
     stat_cor() +
     ylab(paste0(feature," replicate 2 [π]")) +
     xlab(paste0(feature," replicate 1 [π]")) +
     ggtitle(paste0("E(Pc) ","interaction reproducibility")) +
     theme_b110()

#for brm

d <- interaction_stats %>% 
  filter(query_name=="brm") %>% 
    ggplot(aes(x=(`1`+`4`)/2,y=(`2`+`3`)/2)) +
     geom_abline(slope = 1,lty=2) +
     geom_vline(xintercept = 0,lty=2) +
     geom_hline(yintercept = 0,lty=2) +
     geom_point(col=b110_grey) + 
     geom_smooth(col="black",method="rlm") +
     stat_cor() +
     ylab(paste0(feature," replicate 2 [π]")) +
     xlab(paste0(feature," replicate 1 [π]")) +
     ggtitle(paste0("brm ","interaction reproducibility")) +
     theme_b110()


e <-a+b+c+d

ggsave("plots/S1_data_norm_interaction_corr.png",e,width = 24,height = 24,units = "cm")
ggsave("plots/S1_data_norm_interaction_corr.pdf",e,width = 24,height = 24,units = "cm")
```


