---
title: "0-Interaction-bias-correction"
author: "Florian Heigwer"
date: "13/07/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(MASS)
library(tidyverse)
library(patchwork)
library(limma)

call_interactions<-function (x, TP, TargetNeg, QueryNeg, eps = 1e-04, maxiter = 100, na.rm = TRUE){
  if (missing(TP)) {
    MTP = 1
    TP = rep(1, dim(x)[1])
  }
  else {
    MTP = max(TP)
  }
  z <- x
  nr <- nrow(z)
  nc <- ncol(z)
  t <- 0
  r <- numeric(nr)
  c <- matrix(numeric(MTP * nc), nrow = MTP)
  oldsum <- 0
  for (iter in 1L:maxiter) {
    rdelta <- apply(z, 1L, median, na.rm = na.rm)
    z <- z - matrix(rdelta, nrow = nr, ncol = nc)
    r <- r + rdelta
    cdelta <- apply(z, 2L, function(s) {
      tapply(s, TP, median, na.rm = na.rm)
    })
    if (MTP == 1) {
      z <- z - t(matrix(cdelta, nrow = nc, ncol = nr))
    }
    else {
      z <- z - apply(cdelta, 2, function(s) {
        s[TP]
      })
    }
    c <- c + cdelta
    if (missing(QueryNeg)) {
      delta = median(c, na.rm = na.rm)
      if (!is.finite(delta)) {
        delta = 0
      }
    }
    else {
      delta <- mean(c[, QueryNeg], na.rm = TRUE)
      if (!is.finite(delta)) {
        delta = median(c, na.rm = na.rm)
        if (!is.finite(delta)) {
          delta = 0
        }
      }
    }
    c <- c - delta
    t <- t + delta
    if (missing(TargetNeg)) {
      delta = median(r, na.rm = na.rm)
      if (!is.finite(delta)) {
        delta = 0
      }
    }
    else {
      delta <- mean(r[TargetNeg], na.rm = TRUE)
      if (!is.finite(delta)) {
        delta = median(r, na.rm = na.rm)
        if (!is.finite(delta)) {
          delta = 0
        }
      }
    }
    r <- r - delta
    t <- t + delta
    newsum <- sum(abs(z), na.rm = na.rm)
    converged <- newsum == 0 || abs(newsum - oldsum) < eps * 
      newsum
    if (converged) 
      break
    oldsum <- newsum
  }
  if (!converged) {
    warning(gettextf("maineffects() did not converge in %d iterations", 
                     maxiter), domain = NA)
  }
  ans <- list(neg = t, targetMainEffect = r, queryMainEffect = t(c), 
              pi = z)
  ans
}

theme_b110<-function(){
  theme_classic() +
  theme(
    axis.text=element_text(size = 10), 
    axis.title=element_text(size = 10),
    plot.title = element_text(size = 12,hjust = 0.5,face="bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size =10),
    legend.position = "bottom"
    )
}

sgi_blue    = '#5087C8'
sgi_yellow1 = '#F2EE35'
sgi_yellow2 = '#FED98E'
b110_grey   = '#808080'
b110_grey_light   = '#909090'
b110_transparent_black = alpha('#000000',0.5)
google_red='#dd4b39'
google_green='#0F9D58'
google_yellow='#F4B400'
google_blue='#4285F4'

```

## Load example data

For show casing the bias of lethal genes being artificially assigned a positive interaction score by any other semi-lethal gene.

```{r load_data}
load("processed_data/filtered_data_cells.RData")
```

Then we extract the target annotations and reshape the data such that colums are the query genes (dsRNA replicates separate) and rows are target genes (dsRNA replicates separate).

```{r extract_anno}
annotated_data_to_plot_woctrl_wellnorm <- filtered_data

target_annotation<-annotated_data_to_plot_woctrl_wellnorm %>%
  dplyr::select(targetid,fbgn,gene_id) %>%
  distinct() %>% 
  group_by(targetid) %>% 
  do(head(.,n=1)) %>%
  ungroup()

int_data <- filtered_data %>% 
  unite(query_name,query_name,screen) %>%
  spread(query_name,value)
```

Estimate the target and query median effect from the normalized filtered data for later reference as the main effects.

```{r confounder}
  confounder <- filtered_data %>%
    group_by(targetid,query_name) %>%
    group_by(query_name) %>%
    mutate(query_main=median(value,na.rm = T)) %>%
    group_by(targetid) %>%
    mutate(target_main=median(value,na.rm = T)) %>%
    ungroup() %>%
    dplyr::select(-value,-screen,-fbgn,-design,-gene_id) %>%
    distinct() 
```

Now we can call interactions as the residual of a median polish analysis as reported earlier in:

Fischer et al., eLife, 2015;4:e05464 doi: 10.7554/eLife.05464


```{r interaction_calling, echo=FALSE}
 
  interaction <- call_interactions(int_data[,5:ncol(int_data)])

  interaction <- cbind.data.frame(int_data[,1:4],interaction$pi) %>% 
    gather(query_name,value,-fbgn,-design,-gene_id,-targetid) %>% 
    tbl_df() %>% 
    separate(query_name,c("query_name","screen"),sep = "_")
  
  interaction_stats <- 
    interaction %>% 
    group_by(query_name,targetid) %>% 
    mutate(repl=c(1:4)) %>%
    dplyr::select(targetid,query_name,value,repl) %>%
    drop_na() %>%
    ungroup()
  
  interaction_stats<-interaction_stats %>% left_join(confounder) %>% left_join(target_annotation)
  
  interaction_stats_biased<-
    interaction_stats %>% 
    group_by(targetid,query_name) %>% 
    summarise(value=mean(value,na.rm=T),query_main=query_main[1],target_main=target_main[1])
  
```

# Supplemental Figure S4 A-D

Next we are going to visualize if there is a relationship of the remaining residuals of the median polish and the median effects of each target and query.

```{r Example_plot, message=FALSE, warning=FALSE, include=FALSE}

a <- interaction_stats_biased %>%
  filter(query_name=="brm") %>%
  ggplot(aes(x=target_main,y=value)) +
    geom_point() +
    geom_smooth(method = "rlm") +
    theme_b110() +
    ggtitle("main effects vs. pi-scores \n (brm as query)")

b <- interaction_stats_biased %>%
  filter(targetid=="18_G17") %>%
  ggplot(aes(x=query_main,y=value)) +
    geom_point()+
    geom_smooth(method = "rlm") +
    theme_b110() +
    ggtitle("main effects vs. pi-scores \n (brm as target)")

```

As is apparent from this analysis we see a clear correlation between the main-effects of each gene and its ability to form interactions. Especially we see a linear dependency of positive pi-scores and negative main effects.

In a next step we remove this effect by modeling it using a robust linear model separately for each query, estimate a p-value by a moderated one-sample t-test (limma) and finally center and scale the pi-score to make sure that the pi-score distributions of each query follow the approximately same distribution.

```{r}
  fun<-function(x){
    x$combo=x$target_main+x$query_main
    mdl<- rlm(value~combo,data = x)
    x$correction=predict(mdl,x)
    x$correctedpi=x$value-x$correction
    return(x)
  }
  
  interaction_stats %<>% group_by(query_name) %>% do(
    fun(.)
  ) %>%
    dplyr::select(-value,-correction,-combo) %>%
    separate(targetid,c("plate","well"),remove = "F",sep="_") %>%
    group_by(well,query_name) %>%
    mutate(correctedpi=correctedpi-median(correctedpi,na.rm=T)) %>%
    ungroup() %>%
    spread(repl,correctedpi) %>%
    ungroup() %>% 
    mutate(
      pval=eBayes(lmFit(.[,9:12]))$p.value,
      mpi=rowMeans(.[,9:12],na.rm = T)) %>%
    group_by(query_name) %>%
    mutate(mpi=mpi/sd(mpi,na.rm=T)) %>%
    ungroup()
  
  interaction_stats$fdr <- p.adjust(interaction_stats$pval,method = "BH")
```

Finally we visualize the successful removal of the effect.

```{r united_vizualization, message=FALSE, warning=FALSE}

c <- interaction_stats %>%
  filter(query_name=="brm") %>%
  ggplot(aes(x=target_main,y=mpi)) +
    geom_point() +
    geom_smooth(method = "rlm") +
    theme_b110() +
    ggtitle("Corrected: pi-scored vs. main effects \n (brm as query)")

d <- interaction_stats %>%
  filter(query_name=="Cdc23") %>%
  ggplot(aes(x=target_main,y=mpi)) +
    geom_point() +
    geom_smooth(method = "rlm") +
    theme_b110() +
    ggtitle("Corrected: pi-scored vs. main effects \n (Cdc23 as query)")

print(a+b+c+d)

ggsave("plots/S4_interaction_lethal_bias.pdf",width = 15,height = 15,units = "cm")
```

  

