---
title: "0. Syngene_Data_Preprocessing"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(patchwork)
library(MASS)
library(ggridges)
library(tidyverse)

theme_b110<-function(){
  theme_classic() +
  theme(
    axis.text=element_text(size = 10), 
    axis.title=element_text(size = 10),
    plot.title = element_text(size = 12,hjust = 0.5,face="bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size =10),
    legend.position = "bottom"
    )
}

sgi_blue    = '#5087C8'
sgi_yellow1 = '#F2EE35'
sgi_yellow2 = '#FED98E'
b110_grey   = '#808080'
b110_grey_light   = '#909090'
b110_transparent_black = alpha('#000000',0.5)
google_red='#dd4b39'
google_green='#0F9D58'
google_yellow='#F4B400'
google_blue='#4285F4'

```

# Supplemental Figure S4 E-J 

PCA correction reminiscence of normalized morphology and interaction scores

We want to remove the "non-productive RISC binding effect" simultaneously from all features in the gene's interaction scores


```{r}
##1. lets load all the main-effects and interactions stats into one giant tibble
#l=list()
#for(i in list.files("~/raw_data/",pattern = "statistically_tested_pi*.*RData")){
#  print(i)
#  load(paste0("~/raw_data/",i))
#  print("loaded")
#  l[[i]]=interaction_stats
#}

#significant_feature_interactions<-bind_rows(l,.id="feature") %>% mutate(feature=gsub(feature,pattern = "statistically_tested_pi_(.*).RData",replacement = "\\1")) %>% tibble()

#saveRDS(significant_feature_interactions,"processed_data/raw_interaction_stats_all_feats.rds")

raw_interaction_stats_all_feats<-readRDS("processed_data/raw_interaction_stats_all_feats.rds")

```

## feature filtering

Filter for features that were considered reproducible and non-redundant in the first place

```{r}
usable_features<-readRDS("processed_data/usable_features_18112019.rds")

significant_feature_interactions<-raw_interaction_stats_all_feats$. %>% filter(feature%in%usable_features)
```

## data wrangling

now we bring the data into a numeric matrix form amenable to PCA

```{r}
# remove reminescent plate bias in interactions
significant_feature_interactions %<>% 
  group_by(query_name,feature,plate) %>% 
  mutate(mpi=mpi-median(mpi,na.rm=T)) %>% 
  ungroup()

# spread by target quey combination as column and targets as rows
target_x_query.feature<-
  significant_feature_interactions %>% 
  dplyr::select(feature,mpi,targetid,gene_symbol,query_name) %>% 
  unite(feature,feature,query_name,sep = "öö") %>% 
  spread(feature,mpi,fill = 0)

#identify the clusters and annotated the targerts accordingly
N_cluster <- readRDS("processed_data/N_cluster.rds")
Stam_cluster <- readRDS("processed_data/Stam_cluster.rds")

target_x_query.feature <- 
  target_x_query.feature %>% 
  mutate(is_biased=if_else(gene_symbol %in% N_cluster,"N_cluster",
                          if_else(gene_symbol %in% Stam_cluster,"Stam_cluster","ok")))

# separate the numeric matrix and the annotation columns
target_x_query.feature.numeric<-
  target_x_query.feature %>% 
  select_if(is.numeric) %>% 
  as.data.frame()

target_x_query.feature.anno<-
  target_x_query.feature %>% 
  select_if(is.character)

target_x_query.feature.anno <- 
  target_x_query.feature.anno %>% separate(targetid,c("plate","well"),remove = F)
```

We check if the interactions between the clusters are non-specifically different. 

```{r}
plot_interaction_counts <- significant_feature_interactions %>% 
  filter(feature=="cells") %>%
  mutate(is_biased=if_else(gene_symbol %in% N_cluster,"N_cluster",
                          if_else(gene_symbol %in% Stam_cluster,"Stam_cluster","ok")),
         direction=factor(sign(mpi))) %>%
  filter(fdr<0.2) %>%
  ggplot(aes(x=is_biased,grp=direction,fill=direction)) +
    geom_bar(position = "fill") +
      theme_b110() +
      scale_fill_manual(values = c(sgi_blue,sgi_yellow2))
```

We found that indeed the N_cluster contains over proportionally many postive significant interactions while the Stam cluster contains mainly genes exhibiting negative interactions.

## PCA

next we perform PCA and test which principle components separate the mean of the two undesired clusters best

```{r}

# perform conventional PCA on the numeric features
pca_int_biased<-princomp(target_x_query.feature.numeric)

# find which principle components separate the two clusters best such that they can be whitened
separation=seq(1,ncol(pca_int_biased$scores))
for(i in 1:ncol(pca_int_biased$scores)){
  separation[i]<-
    abs(mean(pca_int_biased$scores[which(target_x_query.feature$is_biased=="N_cluster"),i])-
          mean(pca_int_biased$scores[which(target_x_query.feature$is_biased=="Stam_cluster"),i]))
}

# find the two top components separating the two clusters
highest_separation_pca <- head(order(separation,decreasing = T),2)
```

We identified components 1 and 3 as capturing most of the variance that results from the competitive RISC binding phenomenon. Next we visualize this in a scatter plot of these principle components.

```{r}

  data_to_plot_biased <- cbind.data.frame(target_x_query.feature[,1:2],
                     "is_biased"=target_x_query.feature$is_biased,
                     pca_int_biased$scores[,c(3,1)]) %>% 
                  mutate(is_biased=factor(is_biased,c("ok","N_cluster","Stam_cluster"))) 

  plot_biased <- data_to_plot_biased %>%
                  ggplot(aes(x=Comp.3,y=Comp.1,key=gene_symbol,col=is_biased)) + 
                    geom_point(data = data_to_plot_biased %>% filter(is_biased == "ok")) +
                    geom_point(data = data_to_plot_biased %>% filter(is_biased == "N_cluster")) +
                    geom_point(data = data_to_plot_biased %>% filter(is_biased == "Stam_cluster")) +
                    scale_color_manual(values = c(google_red,b110_transparent_black,google_blue)) +
                    theme_b110() +
                    ggtitle("Components capturing the undesired bias")

```

## PCA-whitening

```{r}
# now e transform the original feature data into PC-space

corrected_value<- as.matrix(target_x_query.feature.numeric) %*% pca_int_biased$loadings

# and set the detected components to 0 variance

corrected_value[,head(order(separation,decreasing = T),2)] <-0

# next we transform the data back to feature interaction space by the transposed PC loadings

corrected_value<-corrected_value %*% t(pca_int_biased$loadings)

target_x_query.feature_corrected <- cbind.data.frame(target_x_query.feature.anno[,1:4],corrected_value) %>% tbl_df()

```

Next we want to vizualize if the separation has succesfully been removed.

```{r}
pca_corrected<-princomp(corrected_value)

  data_to_plot_corrected <- cbind.data.frame(target_x_query.feature[,1:2],
                     "is_biased"=target_x_query.feature$is_biased,
                     pca_corrected$scores[,c(3,1)]) %>% 
                  mutate(is_biased=factor(is_biased,c("ok","N_cluster","Stam_cluster"))) 

  plot_corrected <- data_to_plot_corrected %>%
                    ggplot(aes(x=Comp.3,y=Comp.1,key=gene_symbol,col=is_biased)) + 
                      geom_point(data = data_to_plot_corrected %>% filter(is_biased == "ok")) +
                      geom_point(data = data_to_plot_corrected %>% filter(is_biased == "N_cluster")) +
                      geom_point(data = data_to_plot_corrected %>% filter(is_biased == "Stam_cluster")) +
                      scale_color_manual(values = c(google_red,b110_transparent_black,google_blue)) +
                      theme_b110() +
                      ggtitle("Corrected: Components capturing \n the undesired bias")


```

Now we join the corrected interaction values back to the orginial data, reset all 0 to NA and all values that were masked NA before back to NA.

```{r}
target_x_query.feature_corrected %<>% 
  gather(feature_query,normedpi,-targetid,-gene_symbol,-plate,-well) %>%
  tidyr::separate(feature_query,c("feature","query_name"),sep="öö")

significant_feature_interactions <- 
  significant_feature_interactions %>%
  left_join(target_x_query.feature_corrected)

significant_feature_interactions %<>%
  mutate(normedpi=if_else(normedpi==0,NA_real_,normedpi)) %>%
  mutate(normedpi=if_else(is.na(mpi),NA_real_,normedpi)) %>%
  #filter(is.na(normedpi))
  mutate(mpi=normedpi) %>%
  select(-normedpi) 

#write_rds(significant_feature_interactions,path = "processed_data/interactions_stats_all_feats_df_18112019.rds")
```

#PCA of cell number influence on cell mophology based on lethal and non-lethal genes

We further tested if such effects are similarly apparent on the estimated main effects of all genes across the chosen features. We found in initial clustering of the data that there is a dichotomy grouping genes into those that are known lethal genes and those that do not strongly affect cell numbers. Thus we followed the same strategy as before.


## data wrangling

First we selected the genes with the most striking clustering among those groups.
```{r}
#significant_feature_interactions <- readRDS("processed_data/interactions_stats_all_feats_df_18112019.rds")

lethal_genes<-readRDS("processed_data/lethal_genes.rds")
nonlethal_genes<-readRDS("processed_data/nonlethal_genes.rds")

main_effects<-significant_feature_interactions %>% dplyr::select(targetid,gene_symbol,feature, target_main) %>% distinct()

# main effects still need to be centered and scaled

main_effects <- main_effects %>%
                  group_by(feature) %>%
                  mutate(target_main=(target_main-median(target_main,na.rm=T))) %>%
                  ungroup()

plot_main_effect_grouping <- main_effects %>% 
  mutate(is_lethal=if_else(gene_symbol %in% lethal_genes,"lethal",if_else(gene_symbol %in% nonlethal_genes,"non-lethal","else"))) %>%
  filter(feature=="cells",is_lethal!="else") %>%
    ggplot(aes(target_main,fill=is_lethal)) +
      geom_histogram(bins = 100) +
      #ggsignif::geom_signif(comparisons = list(c("lethal","non-lethal"))) +
      theme_b110() +
      ylab("frequency") +
      xlab("cell count (z-score)") +
      scale_fill_manual(values = c(google_red,google_blue))

```

We find a significant bias on cell count separating the two groups and thus investigated which principle component is able to capture this effect.

## PCA

```{r}

main_effect_df <- main_effects %>% 
  spread(feature,target_main) %>% 
  mutate(is_lethal=if_else(gene_symbol %in% lethal_genes,"lethal",if_else(gene_symbol %in% nonlethal_genes,"non-lethal","else")))

main_effect_df.numeric<-main_effect_df %>% select_if(is.numeric) %>% as.data.frame()

main_effect_df.anno <- main_effect_df %>% select_if(is.character)

main_effect_df.anno <- main_effect_df.anno %>% separate(targetid,c("plate","well"),remove = F)

pca<-princomp(main_effect_df.numeric)

separation=seq(1,ncol(pca$scores))
for(i in 1:ncol(pca$scores)){
  separation[i]<-abs(mean(pca$scores[which(main_effect_df$is_lethal=="non-lethal"),i])-mean(pca$scores[which(main_effect_df$is_lethal=="lethal"),i]))
}

head(order(separation,decreasing = T),2)
```

## visualize

Now we can visualize the components that show the highest separation between the two clusters.

```{r}
data_to_plot <- cbind.data.frame(main_effect_df[,1:2],
                                 main_effect_df[,"cells"],
                                "is_lethal"=main_effect_df$is_lethal,
                                pca$scores[,c(1,2)]) %>% 
  mutate(is_biased=factor(is_lethal,c("else","lethal","non-lethal")))

plot_main_effect_pca<-
  data_to_plot %>%
    ggplot(aes(x=Comp.1,y=Comp.2,key=gene_symbol,col=is_lethal)) + 
    geom_point(data = data_to_plot %>% filter(is_lethal == "else")) +
    geom_point(data = data_to_plot %>% filter(is_lethal == "lethal")) +
    geom_point(data = data_to_plot %>% filter(is_lethal == "non-lethal")) +
    scale_color_manual(values = c(b110_transparent_black,google_red,google_blue)) +
    theme_b110() +
    ggtitle("Components capturing \n the cell count effect")

plot_corr_cells_pca<- 
  data_to_plot %>%
  ggplot(aes(x=Comp.1,y=cells,key=gene_symbol,col=is_lethal)) + 
    geom_point(data = data_to_plot %>% filter(is_lethal == "else")) +
    geom_point(data = data_to_plot %>% filter(is_lethal == "lethal")) +
    geom_point(data = data_to_plot %>% filter(is_lethal == "non-lethal")) +
    scale_color_manual(values = c(b110_transparent_black,google_red,google_blue)) +
    theme_b110() +
    ggtitle("Components capturing \n the cell count effect") 

```

The PCA shows that these two clusters can be separated by using only PC1 and PC2 mainly driven by cell number. 
 
Considering this, we hypothesized that for clustering genes by correlation of their morphological phenotype we need to exclude this information and focus on the remaining signal, else the clustering would be mainly reflecting the genes importance for cell proliferation and survival rather than it function in a distinct bioprocess.

## PCA whitening

Thus we want to remove the viability effect simultaneously from all features in the gene's main effects.

```{r}

corrected_value<- as.matrix(main_effect_df.numeric) %*% pca$loadings

corrected_value[,head(order(separation,decreasing = T),2)] <-0

corrected_value<-corrected_value %*% t(pca$loadings)

main_effect_df_corrected_matrix<-cbind.data.frame(main_effect_df.anno[,1:4],corrected_value) %>% as_tibble()

main_effect_df_corrected <- main_effect_df_corrected_matrix %>% gather(feature,value,-targetid,-gene_symbol,-plate,-well) 

main_effect_df_corrected_avg <- 
  main_effect_df_corrected %>% 
  dplyr::select(-plate,-well) %>% 
  group_by(targetid,gene_symbol,feature) %>% 
  summarise(value=mean(value,na.rm=T)) %>% 
  ungroup()

main_effect_df_corrected_avg  %<>% group_by(feature) %>% mutate(value=(value-mean(value,na.rm = T))/sd(value,na.rm=T)) %>% ungroup()
  
#write_rds(main_effect_df_corrected_avg, path = "processed_data/main_effect_df_181119.rds")

```

## figure creation

```{r vizualization, fig.height=7, fig.width=6, message=FALSE, warning=FALSE, paged.print=FALSE}

plot_full <- 
  plot_interaction_counts + 
  plot_biased + 
  plot_corrected + 
  plot_main_effect_grouping + 
  plot_main_effect_pca + 
  plot_corr_cells_pca

print(plot_full)

ggsave(plot = plot_full,filename = "plots/S4_PCA_whitening.pdf",width = 15,height = 12,units = "cm")

```

