---
output: html_document
editor_options: 
  chunk_output_type: console
---
q---
title: "Figure_1_QC"
output: html_document
editor_options: 
  chunk_output_type: console
---

## SETUP

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(patchwork)
library(ggridges)
library(corrr)
library(RColorBrewer)
library(ggrastr)
```

## B110 Theme

```{r theme, include=FALSE}

theme_b110<-function(){
  theme_classic() +
  theme(
    axis.text=element_text(size = 10,family = "Helvetica"), 
    axis.title=element_text(size = 10,family = "Helvetica"),
    plot.title = element_text(size = 12,hjust = 0.5,face="bold",family = "Helvetica"),
    legend.title = element_text(size = 12,family = "Helvetica"),
    legend.text = element_text(size =10,family = "Helvetica"),
    legend.position = "bottom"
    )
}

sgi_blue    = '#5087C8'
sgi_yellow1 = '#F2EE35'
sgi_yellow2 = '#FED98E'
b110_grey   = '#808080'
b110_grey_light   = '#909090'
b110_transparent_black = alpha('#000000',0.5)
google_red='#dd4b39'
google_green='#0F9D58'
google_yellow='#F4B400'
google_blue='#4285F4'

```

# Data read in

```{r}

interaction_vecs<-read_rds("processed_data/interactions_stats_all_feats_df_18112019.rds")

load("processed_data/normalized_data_cells.RData")

filtered_data_cor_many_feats<-readRDS("processed_data/cor_many_feats_18112019.rds")

```

## Supplementary Figure 16 A

Normed feature correlation between replicate screens (different query RNAi reagents)

```{r}

p1 <- filtered_data_cor_many_feats %>%
    group_by(feature) %>%
    filter(median(c)>0.5) %>%
    ggplot(aes(x=c,y=reorder(feature,-c,median,na.rm=T))) +
      geom_density_ridges(lwd=0.1,col=b110_grey) +
      geom_vline(xintercept = 0.5,col=google_red) +
      xlim(0,1) +
      theme_b110() +
      theme(axis.text.y=element_blank(),axis.ticks.y=element_blank()) +
      ylab("features")

ggsave(p1,filename = "all_feature_normed_value_replicate_correlations.pdf",width = 6,height = 30,units = "cm")



```


## Supplementary Figure 16 B

Correlation of interaction profiles across different queries and RNAi designs

```{r}

f1<-function(x){
  cor((x[,"2"]+x[,"3"])/2,(x[,"1"]+x[,"4"])/2,method = "p",use="p")
}

f2<-function(x){
  cor((x[,"1"]+x[,"2"])/2,(x[,"3"]+x[,"4"])/2,method = "p",use="p")
}

f3<-function(x){
  cor((x[,"1"]+x[,"3"])/2,(x[,"2"]+x[,"4"])/2,method = "p",use="p")
}

f4<-function(x){
  cor((x[,"1"]),(x[,"2"]),method = "p",use="p")
}

f5<-function(x){
  cor((x[,"3"]),(x[,"4"]),method = "p",use="p")
}

f6<-function(x){
  cor((x[,"1"]),(x[,"3"]),method = "p",use="p")
}

f7<-function(x){
  cor((x[,"2"]),(x[,"4"]),method = "p",use="p")
}

statistically_tested_pi_cor<-interaction_vecs %>% 
                                filter(feature=="cells") %>%
                                group_by(feature,query_name) %>% 
                                do(t2q1.m.t1q2_v_t1q1.m.t2q2=f1(.),t1q1.m.t2q1_v_t1q2t2q2=f2(.),t1q1.m.t1q2_v_t2q1.m.t2q2=f3(.),t1q1_v_t2q1=f4(.),t1q2_v_t2q2=f5(.),t1q1_v_t1q2=f6(.),t2q1_v_t2q2=f7(.)) %>% 
                                unnest(c(t1q1_v_t1q2, t2q1_v_t2q2, t1q1_v_t2q1, t1q2_v_t2q2, t1q1.m.t1q2_v_t2q1.m.t2q2,t1q1.m.t2q1_v_t1q2t2q2, t2q1.m.t1q2_v_t1q1.m.t2q2)) %>% 
                                gather(type,value,-query_name,-feature) %>%
                                mutate(
                                  type=
                                    factor(type,
                                              levels=c("t1q1_v_t1q2", "t2q1_v_t2q2", "t1q1_v_t2q1", "t1q2_v_t2q2", "t1q1.m.t1q2_v_t2q1.m.t2q2","t1q1.m.t2q1_v_t1q2t2q2", "t2q1.m.t1q2_v_t1q1.m.t2q2")))

medians <- statistically_tested_pi_cor %>% 
  group_by(type) %>%
  summarise(value=median(value)) 

p2 <- statistically_tested_pi_cor %>%
  ggplot(aes(value)) +
    geom_density() +
    xlim(-0.5,1) +
    geom_vline(xintercept = 0,lty=2) +
    geom_vline(data = medians, aes(xintercept = value),lty=1) +
    facet_wrap(~type) +
    theme_b110()
    

ggsave(p2,filename = "cell_number_interaction_profiles_correlations.pdf",width = 16,height = 10,units = "cm")


```

## Supplementary Figure 16 C

Correlation of Interaction permutations

```{r}

data_subset<-
  interaction_vecs %>% 
  filter(feature=="cells") %>%
  filter(gene_symbol %in% unique(.$query_name)) %>% 
  filter(query_name %in% unique(.$gene_symbol)) %>% 
  mutate(mpi=`1`+`2`+`3`+`4`) %>%
  dplyr::select(query_name,gene_symbol,mpi) %>% 
  arrange(query_name,gene_symbol) %>% 
  group_by(query_name,gene_symbol) %>% 
  summarise(mpi=mean(mpi,na.rm=T)) %>%
  ungroup()

combinations<-
  combn(unique(data_subset$gene_symbol),2) %>% 
  t() %>% 
  as_tibble() %>%
  rename(query_name=V1,gene_symbol=V2) %>% 
  left_join(data_subset) %>% 
  dplyr::rename(gene_symbol="query_name",query_name="gene_symbol",QxT=mpi) %>% 
  left_join(data_subset) %>% 
  dplyr::rename(TxQ ="mpi")

p3<-combinations %>% 
  ggplot(aes(x=QxT,y=TxQ)) +
    geom_abline(slope = 1,lty=2,lwd=0.5) +
     geom_vline(xintercept = 0,lty=2) +
     geom_hline(yintercept = 0,lty=2) +
     geom_point_rast(col=b110_grey, size = 0.5) + 
     stat_cor(method = "pearson") +
     ylab(paste0("QxT [π]")) +
     xlab(paste0("TxQ [π]")) +
     ggtitle(paste0("interaction permutation")) +
     theme_b110()

ggsave(p3,filename = "cell_number_interaction_permutation_correlation.pdf",width = 10,height = 10,units = "cm")

```


