---
title: "SYNGENE_analysis_correlation_analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

## SETUP

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(PRROC)
library(ggrastr)
library(patchwork)
library(ggrepel)
library(MASS)
```

## Loading cell number data 

```{r}
usable_features<-readRDS("processed_data/usable_features_18112019.rds")
main_effects_df <- read_rds("processed_data/main_effect_df_181119.rds")
interaction_vecs<-read_rds("processed_data/interactions_stats_all_feats_df_18112019.rds")
translator<-read_delim("annotations/translator.txt",delim = "\t")

interaction_vecs %<>% left_join(translator) %>% filter(feature %in% usable_features)
main_effects_df %<>% left_join(translator) %>% filter(feature %in% usable_features)
interaction_stats<-interaction_vecs %>% filter(feature=="cells")
```

# get the annotations for safe and all other benchmarks and training (GO terms, gene groups and protein complexes) based on gene_symbol

```{R } 

genes_to_ids<- translator %>% dplyr::select(current_fbgn=converted_id,current_symbol,targetid)

genes_to_GO<-read_delim("annotations/gene_information.txt",delim="\t") %>% dplyr::select(go_id,current_fbgn=fbgn)

GO_to_words<-read_delim("annotations/goterms.txt",delim = "\t")

genes_to_genegroups<-read_delim("annotations/gene_group_data_fb_2019_02_mod.tsv",delim = "\t") %>% dplyr::select(gene_group=FB_group_name,current_symbol=Group_member_FB_gene_symbol,current_fbgn=Group_member_FB_gene_id)

load("annotations/Complexes_from_paper.RData")

gene_group_LUT<-genes_to_genegroups %>% split(.$current_symbol)

gene_GO_LUT<-genes_to_ids %>% left_join(genes_to_GO) %>% dplyr::select(current_symbol,go_id) %>% distinct() %>% split(.$current_symbol)

complex_LUT<-complexes %>% ungroup() %>% dplyr::select(current_fbgn=member,complex) %>% left_join(genes_to_ids) %>% dplyr::select(current_symbol,complex) %>% split(.$current_symbol)

genes_to_ids %>% 
  left_join(genes_to_GO) %>% 
  left_join(GO_to_words) %>% 
  dplyr::select(current_fbgn,current_symbol,targetid,go_term) %>% 
  distinct() %>% mutate(current_fbgn=1) %>% 
  spread(go_term,current_fbgn,fill=0) %>% 
  dplyr::select(-targetid) %>% 
  write_delim("annotations/SAFE_format_GO.txt",delim="\t")

genes_to_ids %>% 
  left_join(genes_to_genegroups) %>% 
  dplyr::select(current_fbgn,current_symbol,targetid,gene_group) %>% 
  distinct() %>% 
  mutate(current_fbgn=1) %>% 
  spread(gene_group,current_fbgn,fill=0) %>% 
  dplyr::select(-targetid) %>% 
  write_delim("annotations/SAFE_format_GG.txt",delim="\t")
```

## Figure 1E

Plotting a global interaction profile correlation based network

  # Compute all pair-wise GI profile correlations using pearson correlation

```{r}
GI_corrs<-interaction_vecs %>% 
  filter(feature=="cells") %>%
  unite(current_symbol,current_symbol,targetid,sep="öö") %>% 
  dplyr::select(query_name,mpi,current_symbol) %>% 
  spread(current_symbol,mpi) %>%
  dplyr::select(-query_name) %>%
  corrr::correlate(method = "p",use="p") %>%
  corrr::shave() %>%
  corrr::stretch() %>%
  drop_na()

GI_corrs %>%
  filter(r>0.45) %>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,idx,idy,r) %>%
  write_delim("processed_data/correlation_table_simple_0.45_filtered_genes_v4.txt",delim = "\t")


corr_filter<-function(gene){
  GI_corrs %>% 
    ungroup() %>%
    filter(r>0.3,(x==gene | y==gene)) %>%
    arrange(desc(r)) %>% 
    head(n=3) %>% 
    return()
}

all_genes<-c(GI_corrs$x,GI_corrs$y) %>% unique()

filtered_corrs<-lapply(all_genes, corr_filter)

filtered_corrs<-bind_rows(filtered_corrs) %>% distinct()

filtered_corrs %<>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,idx,idy,r)


write_delim(x = filtered_corrs,"processed_data/correlation_table_pan_0.3_first3_filtered_genes_v3.txt",delim = "\t")

```

## extra get combined corrs

```{r}

combined_corrs<-interaction_vecs %>% 
  unite(current_symbol,current_symbol,targetid,sep = 'öö') %>% 
  unite(query_name,query_name,feature) %>%
  dplyr::select(value=mpi,current_symbol,query_name) %>%
  distinct() %>%
  spread(current_symbol,value) %>%
  dplyr::select(-query_name) %>%
  corrr::correlate(method = "p",use="p") %>%
  corrr::shave() %>%
  corrr::stretch() %>%
  drop_na()

filtered_combined_corrs<-combined_corrs %>% 
    ungroup() %>%
    filter(r>0.2)

corr_filter<-function(gene){
  filtered_combined_corrs %>% 
    filter(x==gene | y==gene) %>%
    arrange(desc(r)) %>% 
    head(n=3) %>% 
    return()
}

all_genes<-c(combined_corrs$x,combined_corrs$y) %>% unique()

filtered_combined_corrs<-lapply(all_genes, corr_filter)

filtered_combined_corrs<-bind_rows(filtered_combined_corrs) %>% distinct()

filtered_combined_corrs %<>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,r)

write_delim(x = filtered_combined_corrs,"processed_data/correlation_table_pan_combined_0.2_first3_v2.txt",delim = "\t")

combined_corrs %>%
  filter(r>0.3) %>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,r) %>%
  write_delim("processed_data/correlation_comb_table_simple_0.3.txt",delim = "\t")


```

## Main effect correlations

```{r cars}

feature_corrs<-main_effects_df %>% 
  unite(current_symbol,current_symbol,targetid,sep='öö') %>% 
  dplyr::select(feature,value,current_symbol) %>%
  distinct() %>%
  spread(current_symbol,value) %>%
  dplyr::select(-feature) %>%
  corrr::correlate(method = "p",use="p") %>%
  corrr::shave() %>%
  corrr::stretch() %>%
  drop_na()


corr_filter<-function(gene){
  feature_corrs %>% 
    ungroup() %>%
    filter(r>0.3,(x==gene | y==gene)) %>%
    arrange(desc(r)) %>% 
    head(n=3) %>% 
    return()
}

all_genes<-c(feature_corrs$x,feature_corrs$y) %>% unique()

filtered_feature_corrs<-lapply(all_genes, corr_filter)

filtered_feature_corrs<-bind_rows(filtered_feature_corrs) %>% distinct()

filtered_feature_corrs %<>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,r)


write_delim(x = filtered_feature_corrs,"processed_data/correlation_feat_table_pan_0.3_first2.txt",delim = "\t")

feature_corrs %>%
  filter(r>0.9) %>%
  separate(x,c("genex","idx"),sep = "öö")%>%
  separate(y,c("geney","idy"),sep = "öö") %>%
  dplyr::select(genex,geney,r) %>%
  write_delim("processed_data/correlation_feat_table_simple_0.9.txt",delim = "\t")

```

